 ---
title: "additonal_anlaysis_bud_resubmit"
output: html_document
date: '2022-08-16'
---

misc script fro small anlysis

# setup

## Directories and defaults
```{r setup}
rm(list=ls())
# relative directories
robj<-"r_objects"
fig<-"../../figures"
gis_data<-"../../data/gis_data"
output<-"../../output"

sst_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_sst_netcdf"
chl_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_chl_netcdf"
 
#absolute directory
# drop_img<-"/home/brandon/Dropbox/MERCED/dissertation/presentations/images"

knitr::opts_chunk$set(echo =FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```


## packages and working directory
```{r}
wd<-getwd()

f.ipak <- function(pkg){
  # loads packages, quietly, given by a vector of package names e.g., pkg<-c("ggplot", "tidyverse")
  # will install  packages listed , and their dependencies, if needed.
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE, quiet=T, verbose = F)
  sapply(pkg, require, character.only = TRUE, quietly = FALSE, warn.conflicts=F)
}

# packages<-c("stars", "gridExtra", "cowplot", "sf", "ggspatial","stringr","sp", "rgdal",  "rgeos", "raster","readr" ,"tidyverse", "ggplot2", "lubridate",  "ggthemes", "data.table", "reshape2", "RColorBrewer", "marmap", "extrafont", "oce", "MODIS", "measurements")  # set packages here
# tidyverse: is all of the following packages: ggplot2, dplyr, tidyr, readr, purr, tibble, sringr, & forcats.

packages<-c("sp", "rgdal",  "rgeos", "raster", "readr", "tidyverse", "lubridate",  "ggthemes",  "sf", "cmocean", "ncdf4", "RNetCDF",  "plot3D", "tidync", "devtools", "stars", "ncmeta", "maps", "oce", "data.table", "fasterize", "RStoolbox", "scales", "purrr", "HURDAT", "ggpattern")

# "HURDAT",

f.ipak(packages)
# lapply(packages, require, character.only = TRUE)
# rm(f.ipak, packages)
print(paste0("Current Working Directory is ", getwd()))

```


# common load items:

-gis
-stations

```{r}
# coastline
setwd(wd)
setwd(gis_data)
coastline<-st_read("./ne_50m_land/ne_50m_land.shp") 
# ocean<-st_read("./ne_50m_ocean/ne_50m_ocean.shp") 
cl<-st_crop(coastline, xmin=-170, ymin=-20, xmax=-80, ymax=40)
rm(coastline)
 m.coast <- ggplot()+ geom_sf(data =cl, size=0.5)+ theme(axis.title.x=element_blank(), axis.title.y=element_blank())+
  theme_bw()+ theme(text = element_text(size =12)) 

 # stations
setwd(wd)
setwd(robj)
stations_positions_list<-readRDS("OC1806A_stations_positions_list.R")

stations<-stations_positions_list$ctd_centroids
rm(stations_positions_list)

```


# Aletta

## load  hurdat
- select  Bud and Aletta

```{r}
setwd(wd)
setwd(robj)
# h<-get_hurdat(basin="EP")
# saveRDS(h, "hurdat.R")

h<-readRDS("hurdat.R")
h$DateTime<-with_tz(h$DateTime, tz="UTC")
conv<-1.94384 # convert to m/s

storm_name<-"ALETTA"
a<-filter(h, Name == storm_name& year(DateTime) == 2018)
a$max_sustained_wind_m_s<-a$Wind/conv
h.pts<- sf::st_as_sf(a, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
a.pts<-h.pts

storm_name<-"BUD"
b<-filter(h, Name == storm_name & year(DateTime) == 2018)
b$max_sustained_wind_m_s<-b$Wind/conv
h.pts<- sf::st_as_sf(b, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
b.pts<-h.pts

rm(h.pts)


```


temp saving list object for plotting
```{r}
setwd(wd)
setwd(robj)

tracks_ab<-vector(mode="list", length=2)
tracks_ab[[1]]<-a.pts
tracks_ab[[2]]<-b.pts
names(tracks_ab)<-c("aletta", "bud")
saveRDS(tracks_ab, "tracks_ab.R")

```


## TS and wind speeds
- taken from "GRL_Data_Input_and_Analysis.Rmd"
--## hurricane metrics
-- covnert to MDT after calculations, might explain errors in original bud calulation
** need to compare this


```{r}

a.sp<-SpatialPointsDataFrame(coords = cbind(a$Lat, a$Lon), proj4string =CRS("+proj=longlat") , data = a)
y <- sp::spDists(a.sp, longlat=T, segments=T)
a$distance<-c(0,y)
y<-subset(a, select=c(DateTime, max_sustained_wind_m_s, distance, Lat, Lon))
y$delta= NA
for(i in seq(1, nrow(y), by=2 )){
  y[i,"delta"] = y[i+1,"delta"] = y[i+1,"DateTime"] - y[i,"DateTime"]
}

y$delta<-shift(y$delta, n=1, fill="NA", type="lag")
y$speed<-(y$distance*1000)/(as.numeric(y$delta)*3600)
y<-y[-1,]
y<-na.omit(y)
a.ts<-y

rm(y)

b.sp<-SpatialPointsDataFrame(coords = cbind(b$Lat, b$Lon), proj4string =CRS("+proj=longlat") , data = b)
y <- sp::spDists(b.sp, longlat=T, segments=T)
b$distance<-c(0,y)
y<-subset(b, select=c(DateTime, max_sustained_wind_m_s, distance, Lat, Lon))
y$delta= NA
for(i in seq(1, nrow(y), by=2 )){
  y[i,"delta"] = y[i+1,"delta"] = y[i+1,"DateTime"] - y[i,"DateTime"]
}

y$delta<-shift(y$delta, n=1, fill="NA", type="lag")
y$speed<-(y$distance*1000)/(as.numeric(y$delta)*3600)
y<-y[-1,]
y<-na.omit(y)

b.ts<-y

rm(y)

round(median(a.ts$speed), 2)
round(median(b.ts$speed), 2)

round(median(a.ts$max_sustained_wind_m_s), 1)
round(median(b.ts$max_sustained_wind_m_s), 1)




```


distance and time match up
```{r}

y<-a.ts
#hardcoding
names(y)[1]<-"time_utc" 
y$time_mdt<-with_tz(y$time_utc, tz="US/Mountain")
row.names(y)<-1:dim(y)[1]
op<-st_as_sf(y, coords = c("Lon", "Lat"),crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

st<-stations
names(st)[4]<-"time_mdt"
st$time_utc<-with_tz(st$time_mdt, tz="UTC")

st<-st_as_sf(st, coords = c("longitude", "latitude"),crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") 


#matching above

op.f<-filter(op, time_mdt<=st$time_mdt[1])
st.f<-st[1,]
match1<-cbind(op[st_nearest_feature(st.f, op.f),], st.f) 
match1$distance_km<-round(as.integer(st_distance(match1$geometry, match1$geometry.1)/1000), 0)
match1<-match1 %>% st_drop_geometry(.) 

op.f<-filter(op, time_mdt<=st$time_mdt[2])
st.f<-st[2,]
match2<-cbind(op[st_nearest_feature(st.f, op.f),], st.f) 
match2$distance_km<-round(as.integer(st_distance(match2$geometry, match2$geometry.1)/1000), 0)
match2<-match2 %>% st_drop_geometry(.) 


op.f<-filter(op, time_mdt<=st$time_mdt[3])
st.f<-st[3,]
match3<-cbind(op[st_nearest_feature(st.f, op.f),], st.f)
match3$distance_km<-round(as.integer(st_distance(match3$geometry, match3$geometry.1)/1000), 0)
match3<-match3 %>% st_drop_geometry(.) 

op.f<-filter(op, time_mdt<=st$time_mdt[4])
st.f<-st[4,]
match3.5<-cbind(op[st_nearest_feature(st.f, op.f),], st.f) 
match3.5$distance_km<-round(as.integer(st_distance(match3.5$geometry, match3.5$geometry.1)/1000), 0)
match3.5<-match3.5 %>% st_drop_geometry(.) 

op.f<-filter(op, time_mdt<=st$time_mdt[5])
st.f<-st[5,]
match4<-cbind(op[st_nearest_feature(st.f, op.f),], st.f)
match4$distance_km<-round(as.integer(st_distance(match4$geometry, match4$geometry.1)/1000), 0)
match4<-match4 %>% st_drop_geometry(.)  

op.f<-filter(op, time_mdt<=st$time_mdt[6])
st.f<-st[6,]
match5<-cbind(op[st_nearest_feature(st.f, op.f),], st.f)
match5$distance_km<-round(as.integer(st_distance(match5$geometry, match5$geometry.1)/1000), 0)
match5<-match5 %>% st_drop_geometry(.) 

matched<-rbind(match1, match2, match3, match3.5, match4, match5)



matched$hours_after<-as.integer(round((matched$time_mdt.1-matched$time_mdt), 1))

matched<-(select(matched, -geometry.1, -time_mdt.1, -time_utc.1))

print(matched)


```


Means of track psoitions near staion 3 Alette

```{r}
a.ts[3:12,] # theser are relevant points

```


calutea wind diameter area:
- make a function
- mean diamter for eash wind speed buffer.
- caluate areas
- stadarized for area/ tracks etc

-jus F it and \-proabb;ly just us apply function

here: https://www.datasciencemadesimple.com/row-wise-median-row-median-in-r-dataframe/



```{r}
# names(a)


x<-a
print((mean(na.omit(x$NE34))+ mean(na.omit(x$SE34)) +mean(na.omit(x$SW34))+mean(na.omit(a$NW34)))/4)
print((mean(na.omit(x$NE50))+ mean(na.omit(x$SE50)) +mean(na.omit(x$SW50))+mean(na.omit(a$NW50)))/4)
print((mean(na.omit(x$NE64))+ mean(na.omit(x$SE64)) +mean(na.omit(x$SW64))+mean(na.omit(a$NW64)))/4)
x<-b
print((mean(na.omit(x$NE34))+ mean(na.omit(x$SE34)) +mean(na.omit(x$SW34))+mean(na.omit(a$NW34)))/4)
print((mean(na.omit(x$NE50))+ mean(na.omit(x$SE50)) +mean(na.omit(x$SW50))+mean(na.omit(a$NW50)))/4)
print((mean(na.omit(x$NE64))+ mean(na.omit(x$SE64)) +mean(na.omit(x$SW64))+mean(na.omit(a$NW64)))/4)

## attmept 2:b.ppts
test<-select(x, Key, Name, DateTime, Lat, Lon, max_sustained_wind_m_s, NE64, SE64, SW64, NW64 )
test<-select(x, DateTime, NE64, SE64, SW64, NW64 )
test$row_median = apply(test[,-1], 1, median)

```



# CTDs and profiles
2017 & 2018

From drive:

"2017 Cast Info
Casts 1-11 are station 7
Casts 12-22 are station 6
Casts 23-33 are station 5
Casts 34-46 are station 4
Casts 47-56 are station 3
Casts 57-69 are station 2
Casts 70-80 are station 1"



```{r}

```

