---
title: "ch1_appendix"
author: "Brandon M. Genco"
date: "`r Sys.Date()`"
output: html_document
---

In order of
1)ADCP
2)CTD casts
3) extra export figs
-signal and noise
-pdo and enso


# setup
```{r setup}
rm(list=ls())

r_scriptwd<-getwd()
wd<-substring(r_scriptwd,1,nchar(r_scriptwd) -10) # hardcoding replace here
knitr::opts_knit$set(root.dir = wd)


# relative directories
robj<-"r_objects"
fig<-"../../figures"
gis_data<-"../../data/gis_data"
output<-"../../output"


knitr::opts_chunk$set(echo =FALSE, warning = FALSE)
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) #deleated local rproj file. giut hub issues
```

## packages and working directory

Installed custom hurdat package using r markdown menu
* download  tar from archive as no longer maintained on cran repository
* https://cran.r-project.org/src/contrib/Archive/HURDAT/
+ include as git submodule instead

```{r}
# wd<-getwd()

f.ipak <- function(pkg){
  # loads packages, quietly, given by a vector of package names e.g., pkg<-c("ggplot", "tidyverse")
  # will install  packages listed , and their dependencies, if needed.
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE, quiet=T, verbose = F)
  sapply(pkg, require, character.only = TRUE, quietly = FALSE, warn.conflicts=F)
}

# packages<-c("stars", "gridExtra", "cowplot", "sf", "ggspatial","stringr","sp", "rgdal",  "rgeos", "raster","readr" ,"tidyverse", "ggplot2", "lubridate",  "ggthemes", "data.table", "reshape2", "RColorBrewer", "marmap", "extrafont", "oce", "MODIS", "measurements")  # set packages here
# tidyverse: is all of the following packages: ggplot2, dplyr, tidyr, readr, purr, tibble, sringr, & forcats.

# remotes::install_github("R-Finance/xtsExtra")

packages<-c("sp", "rgdal",  "rgeos", "raster", "readr", "tidyverse", "lubridate",  "ggthemes",  "sf", "cmocean", "ncdf4", "RNetCDF",  "plot3D", "tidync", "devtools", "stars", "ncmeta", "maps", "oce", "data.table", "fasterize", "RStoolbox", "scales", "purrr", "HURDAT", "ggpattern", "zoo", "xts", "dsa",  "tsibble", "feasts", "tsbox", "rsoi", "cowplot")

# "HURDAT",
# "cowplot.pa")


f.ipak(packages)
# lapply(packages, require, character.only = TRUE)
# rm(f.ipak, packages)
print(paste0("Current Working Directory is ", getwd()))

```


## Functions

```{r}
f.anomaly<-function(c){
  m<-mean(c)
  n<-c-m
  return(n)
}

f.noise<-function(x, h.date, prior, post){

x<-x1
noise<-vector(mode='list', length=(length(h.date)))
# y<-na.omit(x1)

for(i in 1:length(h.date)){
noise[[i]]<-filter(x, between(x$date, (h.date[i]-prior), (h.date[i]+post)))
}

noise<-Filter(Negate(is.null), noise)
noise<-bind_rows(noise)
noise<-filter(noise, duplicated(noise$date)==F)

signal<-x[!x$date %in% noise$date,]
# signal<-filter(x, date!=noise$date)
split<-list(signal, noise)
names(split)<-c("signal", "noise")
return(split)}
```

# adcp
# ctd casts
```{r}
print(getwd())
```

```{r}
setwd(wd)
d.sec<-readRDS("r_objects/OC1806A_ctd_sections.R")
d35<-d.sec$st3.5

c1<-d35@data$station[[1]]

c2<-d35@data$station[[2]]
c3<-d35@data$station[[3]]
c4<-d35@data$station[[4]]
c5<-d35@data$station[[5]]

times<-c(c1@metadata$date, c2@metadata$date, c3@metadata$date, c4@metadata$date, c5@metadata$date) 
times<-ymd_hms(times)%>%with_tz(., tzone="US/Mountain")%>%round_date(., 'minute')%>% as.character(.) %>%as.POSIXct(.)      
times<-format(times, format="%m-%d %H:%M")

# d35@metadata$time<-times

d4<-d.sec$st4



```

### checking dpdp

```{r}
par(mfrow = c(1, 3))



plot(c1, which=2, plim=c(100,0), )
plot(c2, which =6,  plim=c(100,0))
plot(c3, which =6,  plim=c(100,0))

```


## messing around with section plots:

```{r}

plot(d35, which="salinity")
distance <- section[["distance"]]
depth <- section[["depth"]]
spice <- section[["spice"]]
look <- spice > 1.8 & depth > 500
points(distance[look], depth[look], col="red")


plot(d35, which="oxygen2", ztype="points", xtype="time", ylim=c(-20,80), xlab=NULL)
```




```{r}
# need to use local time on these objects. will need to photohsop times


plot(d35, which="oxygen2", ztype="image", xtype="time", ylim=c(-20,80), xlab=NULL)
plot(d35, which=3, ztype="image", xtype="time", ylim=c(-20,80), add=T) # density
plot(d35, which=c("oxygen2", "density"), ztype="point", xtype="time", ylim=c(-20,70)) # density

plot(d35, which=c("oxygen2", "beamAttenuation", "density"), ztype="image", xtype="time", ylim=c(-20,70)) # density
plot(d35, which=c("oxygen2", "beamAttenuation", "density"), ztype="image", xtype="time")

plot(d35, which="fluorescence", ztype="image", xtype="time", ylim=c(-20,80))
plot(d35, which="par", ztype="image", xtype="time", ylim=c(-20,70)) #not neede
plot(d35, which="par", ztype="points", xtype="time", ylim=c(-20,70)) #not needed


# version 2 does not work becuase og grob issue
# plot(d35, which="oxygen2", ztype="image", xtype="time", ylim=c(-20,80))
# pa<-recordPlot()
# plot(d35, which="beamAttenuation", ztype="image", xtype="time", ylim=c(-20,80))
# pb<-recordPlot()
# plot(d35, which="fluorescence", ztype="image", xtype="time", ylim=c(-20,80))
# pc<-recordPlot()
# plot(d35, which="density", ztype="image", xtype="time", ylim=c(-20,80))
# pd<-recordPlot()
# 
# pdf("station_35_section.pdf")
# plot_grid(pa, pb, pc, pd, nrow=2, ncol=2,
#          labels = c('a', 'b', 'c', 'd'), align = "h", scale=.5, greed=T, axis="r")
# dev.off()


plot(d4, which=c("oxygen2", "beamAttenuation","fluorescence","density"), ztype="image", xtype="time", ylim=c(-20,70)) # density


```


```{r}
plot(d4, which="oxygen2", ztype="image", xtype="time", ylim=c(-20,80), xlab=NULL)
plot(d4, which=3, ztype="image", xtype="time", ylim=c(-20,80)) # density

plot(d4, which="fluorescence", ztype="image", xtype="time", ylim=c(-20,80))
plot(d4, which="par", ztype="image", xtype="time", ylim=c(-20,80)) #not needed

st_4times<-ymd_hms(d4@metadata$time)%>%with_tz(., tzone="US/Mountain")%>%round_date(., 'minute')%>% as.character(.) %>%as.POSIXct(.) 

```


```{r}
plot(d35, drawIsobaths=T, which="map")
plot(d35, which=3, ztype="image")
# plot(d35, which="salinity", ztype="image", xtype="time")
# plot(d35, which="temperature", ztype="image", xtype="time")
plot(d35, which="oxygen2", ztype="image", xtype="time")
plot(d35, which="fluorescence", ztype="image", xtype="time")

```

## individual plots


corelation

# other plots
```{r}
plot(c2, which=c("oxygen2", 6), type="l")
plot(c2, which=c("oxygen2", 2), type="l")
plot(c2, which=c("oxygen2", 6, "temperature", "beamAttenuation"), type="l")
plotProfile(c2, which=c("oxygen2", "temperature", "beamAttenuation"), type="l",ylim=c(0,80))

plotProfile(c2, xtype="density+dddt", type="l", ylim=c(80,10))
            
            
            #Will need to clautlae density

```

##


```{r}
par(mfrow = c(3, 5))

plotProfile(c1, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
plotProfile(c2, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
plotProfile(c3, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
plotProfile(c4, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
plotProfile(c5, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")

plotProfile(c1, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
plotProfile(c2, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
plotProfile(c3, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
plotProfile(c4, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
plotProfile(c5, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")

plotProfile(c1, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
plotProfile(c2, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
plotProfile(c3, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
plotProfile(c4, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
plotProfile(c5, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")

```


#ch1 appendix v1 
```{r}




# main plot do in console
# depth  profiles
par(mfrow = c(3, 2))
plotProfile(c2, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
plotProfile(c2, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
plotProfile(c2, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
plotProfile(c2, xtype="par",ylim=c(80,10), col ="purple", ytype="depth")
plotProfile(c2, xtype="density", ylim=c(80,10), col="brown", ytype="depth")
plotProfile(c2, xtype="temperature", ylim=c(80,10), col="red", ytype="depth")




par(mfrow = c(3, 2))
plotProfile(c2, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
plotProfile(c2, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
plotProfile(c2, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
plotProfile(c2, xtype="par",ylim=c(80,10), col ="purple", ytype="depth")
plotProfile(c2, xtype="density", ylim=c(80,10), col="brown", ytype="depth")
plotProfile(c2, xtype="temperature", ylim=c(80,10), col="red", ytype="depth")


bo<-recordPlot()
pdf("station_35_profiles.pdf", height =9, width=6)
bo
dev.off()

# density profiles
par(mfrow = c(2, 2))
plotProfile(c2, xtype="beamAttenuation",  ytype="sigmaTheta")
plotProfile(c2, xtype="oxygen2",  ytype="sigmaTheta", col="blue")
# plotProfile(c2, xtype="oxygen2",  ytype="sigmaTheta", col="blue")
plotProfile(c2, xtype="fluorescence",col ="green", ytype="sigmaTheta")
plotProfile(c2, xtype="par",  ytype="sigmaTheta", col="purple")
b1<-recordPlot()


pdf("station_35_density_profiles.pdf", height =9, width=8)
b1
dev.off()


par(mfrow = c(2, 2))
plotProfile(c2, xtype="density+N2", ylim=c(80,10),  ytype="depth")
plotProfile(c2, xtype="salinity+temperature", ylim=c(80,10))
plotProfile(c2, xtype="spice", ylim=c(80,10),  ytype="depth")
plotProfile(c2, xtype="Rrho", ylim=c(80,10),  ytype="depth")

b2<-recordPlot()

pdf("station_35_oceanography_profiles.pdf", height =9, width=8)
b2
dev.off()




```


#ch1 appendix v2 

station 3.5

```{r}
plotProfile(c2, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
pa<-recordPlot()
plotProfile(c2, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
pb<-recordPlot()
plotProfile(c2, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
pc<-recordPlot()
plotProfile(c2, xtype="par",ylim=c(80,10), col ="purple", ytype="depth")
pd<-recordPlot()
plotProfile(c2, xtype="density", ylim=c(80,10), col="brown", ytype="depth")
pe<-recordPlot()
plotProfile(c2, xtype="temperature", ylim=c(80,10), col="red", ytype="depth")
pf<-recordPlot()




pdf("station_35_profiles_v3.pdf", height =14.5, width=9.5)

plot_grid(pa, pb, pc, pd, pe, pf, nrow=3, ncol=2,
         labels = c('a', 'b', 'c', 'd', 'e', 'f'), align = "h", scale=.83, greed=T, axis="r")
dev.off()



# par(mfrow = c(2, 2))
plotProfile(c2, xtype="oxygen2",  ytype="sigmaTheta", col="blue")
pa<-recordPlot()
plotProfile(c2, xtype="beamAttenuation",  ytype="sigmaTheta")
pb<-recordPlot()
# plotProfile(c2, xtype="oxygen2",  ytype="sigmaTheta", col="blue")
plotProfile(c2, xtype="fluorescence",col ="green", ytype="sigmaTheta")
pc<-recordPlot()
plotProfile(c2, xtype="par",  ytype="sigmaTheta", col="purple")
pd<-recordPlot()

setwd(wd)
setwd(fig)
pdf("station_35 density_profiles_v2.pdf", height=9, width=8)
plot_grid(pa, pb, pc, pd, nrow=2, ncol=2,
         labels = c('a', 'b', 'c', 'd'), align = "h", scale=1, greed=T, axis="r")
dev.off()


par(mfrow = c(2, 2))
plotProfile(c2, xtype="density+N2", ylim=c(80,10),  ytype="depth")
# pa<-recordPlot()
plotProfile(c2, xtype="salinity+temperature", ylim=c(80,10))
# pb<-recordPlot()
plotProfile(c2, xtype="spice", ylim=c(80,10),  ytype="depth")
# pc<-recordPlot()
plotProfile(c2, xtype="Rrho", ylim=c(80,10),  ytype="depth")
# pd<-recordPlot()


pdf("station_35_oceanography_profiles_v2.pdf", height =9, width=8)
plot_grid(pa, pb, pc, pd, nrow=2, ncol=2,
         labels = c('a', 'b', 'c', 'd'), align = "h", scale=.8, greed=T, axis="r")
dev.off()





```

### time seris of focus plots

```{r}
 # dev.off()
par(mfrow = c(3, 5), oma=c(3,0,0,0), mar=c(5,0,0,0))

plotProfile(c1, xtype="oxygen2",  ytype="sigmaTheta", col="blue", ylim=c(26.5,25))
mtext("Cast 1", side=3, line=3, outer =T)

plotProfile(c2, xtype="oxygen2",  ytype="sigmaTheta", col="blue", ylim=c(26.5,25))
plotProfile(c3, xtype="oxygen2",  ytype="sigmaTheta", col="blue", ylim=c(26.5,25))
plotProfile(c4, xtype="oxygen2",  ytype="sigmaTheta", col="blue", ylim=c(26.5,25))
plotProfile(c5, xtype="oxygen2",  ytype="sigmaTheta", col="blue", ylim=c(26.5,25))
plotProfile(c1, xtype="beamAttenuation",  ytype="sigmaTheta", col="black", ylim=c(26.5,25))
plotProfile(c2, xtyp="beamAttenuation",  ytype="sigmaTheta", col="black", ylim=c(26.5,25))
plotProfile(c3, xtype="beamAttenuation",  ytype="sigmaTheta", col="black", ylim=c(26.5,25))
plotProfile(c4, xtype="beamAttenuation",  ytype="sigmaTheta", col="black", ylim=c(26.5,25))
plotProfile(c5, xtype="beamAttenuation",  ytype="sigmaTheta", col="black", ylim=c(26.5,25))
plotProfile(c1, xtype="fluorescence",  ytype="sigmaTheta", col="green", ylim=c(26.5,25))
plotProfile(c2, xtyp="fluorescence",  ytype="sigmaTheta", col="green", ylim=c(26.5,25))
plotProfile(c3, xtype="fluorescence",  ytype="sigmaTheta", col="green", ylim=c(26.5,25))
plotProfile(c4, xtype="fluorescence",  ytype="sigmaTheta", col="green", ylim=c(26.5,25))
plotProfile(c5, xtype="fluorescence",  ytype="sigmaTheta", col="green", ylim=c(26.5,25))


```





## stats
```{r}
cor(c2@data$oxygen2, c2@data$beamAttenuation)
```

#ch1 appendi staion 4
```{r}

plotProfile(c1, xtype="oxygen2",ylim=c(80,10), col="blue", ytype= "depth")
pa<-recordPlot()
plotProfile(c1, xtype="beamAttenuation",ylim=c(80,10), col ="black", ytype= "depth")
pb<-recordPlot()
plotProfile(c1, xtype="fluorescence",ylim=c(80,10), col ="green", ytype="depth")
pc<-recordPlot()
plotProfile(c1, xtype="par",ylim=c(80,10), col ="purple", ytype="depth")
pd<-recordPlot()
plotProfile(c1, xtype="density", ylim=c(80,10), col="brown", ytype="depth")
pe<-recordPlot()
plotProfile(c1, xtype="temperature", ylim=c(80,10), col="red", ytype="depth")
pf<-recordPlot()

plot_grid(pa, pb, pc, pd, pe, pf, nrow=3, ncol=2,
         labels = c('a', 'b', 'c', 'd', 'e', 'f'), align = "h", scale=.83, greed=T, axis="r")




```


# export flux
## export flux load data

```{r}
setwd(wd)
setwd(robj)

data<-read_rds("vgpm_integrated_all_years_202200607.R")
x<-data$st3.5
rm(data)

window_area<-round((x$`window_area (m^2)`[1]*1e-6),0)
lab_total<-paste0("Station ", "3.5", ":", " Total Export Flux - ", window_area, " km^2 area")

x$date<-ymd(x$date)
x<-select(x, date, `mean_export_flux (mgC/m^2/day) for_window_area (total/sum_grid_area)`, `total_export_flux (mgC/day)`)
names(x)<-c("date", "avg", "ef")
x$ef<-x$ef/1000000

sst<-readRDS("st35_sst_modis.R")
z<-select(sst, date, `SST_mean (area weighted)`)
rm(sst)
names(z)<-c("date", "sst")
z$date<-ymd(z$date)

chl<-readRDS("st35_chl_modis.R")
y<-select(chl, date, 'chl_mean (area weighted)')
rm(chl)
names(y)<-c("date", "chl")
y$date<-ymd(y$date)

```

## create anomalies
```{r}
x$ef.a<-f.anomaly(x$ef)
x$avg.a<-f.anomaly(x$avg)

y$chl.a<-f.anomaly(y$chl)
z$sst.a<-f.anomaly(z$sst)

xnames<-c("date", "avg_EF_mgC_m2_day", "total_EF_mgC_day", "total_EF_anomaly_mgC_day", "avg_EF_anomaly_mgC_m2_day")
ynames<-c("date", "avg_CHL_mg_m3_day","avg_CHL_anomaly_mg_m3_day")
znames<-c("date", "avg_SST_C", "SST_anomaly_C")

names(x)<-xnames
names(y)<-ynames
names(z)<-znames

# conv<-3.944e+10
# 94.11872*conv

rm(xnames, ynames, znames)

x1<-full_join(y,z, by="date")%>% full_join(., x, by="date")
# missing_values<- x1[rowSums(is.na(x1)) > 0,] # a few misinf vlauers. see august 2020 for export flux
rm(x,y,z)

```
## filled and non-filled dataset

x1= non_filled

```{r}
start<-min(x1$date)
end<-max(x1$date)%>%+7
d<-data.frame(seq(ymd(start), ymd(end), b="days"), NA)
names(d)<-c("date", "remove")


x1[is.na(x1)]<--1 #save an values for later

x2<-full_join(d, x1, by="date") %>% select(., -remove) 
x2<-x2%>% fill(names(x2), .direction =  "down")
x2[x2==-1]<-NA
# rm(x1,d)

```

## spatil selection of storms



#### load hurricanes
## load basic hurdat

```{r}
setwd(wd)
setwd(robj)
#<-get_hurdat(basin="EP")
#saveRDS(h, "hurdat.R")
h<-readRDS("hurdat.R")
h$DateTime<-force_tz(h$DateTime, tz="UTC")

```

#### load POC

```{r}
setwd(wd)
setwd(robj)

data<-read_rds("vgpm_integrated_all_years_202200607.R")
x<-data$st3.5
rm(data)

window_area<-round((x$`window_area (m^2)`[1]*1e-6),0)
lab_total<-paste0("Station ", "3.5", ":", " Total Export Flux - ", window_area, " km^2 area")

x$date<-ymd(x$date)
x<-select(x, date, `mean_export_flux (mgC/m^2/day) for_window_area (total/sum_grid_area)`, `total_export_flux (mgC/day)`)
names(x)<-c("date", "avg", "ef")
x$ef<-x$ef/1000000

sst<-readRDS("st35_sst_modis.R")
z<-select(sst, date, `SST_mean (area weighted)`)
rm(sst)
names(z)<-c("date", "sst")
z$date<-ymd(z$date)

chl<-readRDS("st35_chl_modis.R")
y<-select(chl, date, 'chl_mean (area weighted)')
rm(chl)
names(y)<-c("date", "chl")
y$date<-ymd(y$date)

```



```{r}
# 
 # save_h<-h
# h<-save_h

h<-filter(h, DateTime >=date(min(x2$date))-60) 
h$date<-date(h$DateTime)
h<-select(h, date,Key, Name, Status, Pressure, Wind, Lon, Lat)

# distance<-100000 #200 km
distance<-200000 #400 km

setwd(wd)
setwd(robj)
stations_positions_list<-readRDS("OC1806A_stations_positions_list.R")
st<-stations_positions_list[[3]][4,cbind(2,3)]
st<-sf::st_as_sf(st, coords =c("longitude", "latitude"),  crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
flat<-sf::st_transform(st, "+proj=aeqd +lat_0=18.5005 +lon_0=-108.502" )
circle_3.5<-sf::st_buffer(flat, dist=distance)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
bbox<-st_bbox(circle_3.5)

h.pts<- sf::st_as_sf(h, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
sf::st_crop(., c(xmin=bbox$xmin[[1]], ymin=bbox$ymin[[1]], xmax=bbox$xmax[[1]], ymax=bbox$ymax[[1]])) #subset by user defined 

h<-st_set_geometry(h.pts, NULL)

# smoothing out multi-tiem points


new.h<-h %>% distinct(date, .keep_all = TRUE)


rm(circle_3.5, flat, stations_positions_list, st)

```



## Signal and noise

split date

```{r}
# data<-f.noise(x=x1, h.date=new.h$date, prior=14, post=24)
# conservative, and more accutrate nounds
data<-f.noise(x=x1, h.date=new.h$date, prior=10, post=24)

```

### full times series

```{r}

t<-na.omit(x1) %>%filter(date <= '2020-08-12') 
# t<-na.omit(x1)
t.d<-select(t, date)%>% .[,1]
t<-t%>%select(.,avg_CHL_mg_m3_day, avg_SST_C, avg_EF_mgC_m2_day )
names(t)<-c("CHL", "SST", "EF")

t.sst<-t%>%select(., SST)%>% xts(., t.d)
t.chl<-t%>%select(., CHL)%>% xts(., t.d)
t.ef<-t%>%select(., EF)%>% xts(., t.d)

# trends<-ts_trend(t)
trend.sst<-ts_trend(t.sst)
trend.chl<-ts_trend(t.chl)
trend.ef<-ts_trend(t.ef)

p1<-ts_ggplot(t.chl, ts_trend(t.chl))+scale_color_manual(values = c("darkgreen", "purple"), labels=c("Mean CHL [mg/m3/day]", "Loews Trend"))+ theme_tsbox() + ggtitle("Time Series")
p2<-ts_ggplot(t.sst, ts_trend(t.sst))+scale_color_manual(values = c("red", "purple"), labels=c("Mean SST (째C)", "Loews Trend"))+ theme_tsbox() + ggtitle("Time Series")
p3<-ts_ggplot(t.ef, ts_trend(t.ef))+scale_color_manual(values = c("black", "purple"), labels=c("Mean Export Flux (mgC/m^2/day)", "Loews Trend"))+ theme_tsbox() + ggtitle("Time Series")

```


### signal
```{r}
# x1<-x1 %>% filter(date <= '2020-08-12') 
# t<-(x1)%>%select(.,avg_CHL_mg_m3_day, avg_SST_C, avg_EF_mgC_m2_day )
# t<-na.omit(data$signal) %>%filter(date <= '2020-08-12') 


t<-na.omit(data$signal) %>%filter(date <= '2020-08-12') 
t.d<-select(t, date)%>% .[,1]
t<-(t)%>%select(.,avg_CHL_mg_m3_day, avg_SST_C, avg_EF_mgC_m2_day )
names(t)<-c("CHL", "SST", "EF")

signal.sst<-t%>%select(., SST)%>% xts(., t.d)
signal.chl<-t%>%select(., CHL)%>% xts(., t.d)
signal.ef<-t%>%select(., EF)%>% xts(., t.d)

# trends<-ts_trend(t)

signal_trend.sst<-ts_trend(signal.sst)
signal_trend.chl<-ts_trend(signal.chl)
signal_trend.ef<-ts_trend(signal.ef)

p4<-ts_ggplot(signal.chl, ts_trend(signal.chl))+scale_color_manual(values = c("darkgreen", "purple"), labels=c("Mean CHL [mg/m3/day]", "Loews Trend"))+ theme_tsbox()+ ggtitle("Non TC signal component")
p5<-ts_ggplot(signal.sst, ts_trend(signal.sst))+scale_color_manual(values = c("red", "purple"), labels=c("Mean SST (째C)", "Loews Trend"))+ theme_tsbox() + ggtitle("Non TC signal component") 
p6<-ts_ggplot(signal.ef, ts_trend(signal.ef))+scale_color_manual(values = c("black", "purple"), labels=c("Mean Export Flux (mgC/m^2/day)", "Loews Trend"))+ theme_tsbox() + ggtitle("Non TC signal component")


```

### noise

```{r}

t<-na.omit(data$noise) %>%filter(date <= '2020-08-12') 
t.d<-select(t, date)%>% .[,1]
t<-(t)%>%select(.,avg_CHL_mg_m3_day, avg_SST_C, avg_EF_mgC_m2_day )
names(t)<-c("CHL", "SST", "EF")

noise.sst<-t%>%select(., SST)%>% xts(., t.d)
noise.chl<-t%>%select(., CHL)%>% xts(., t.d)
noise.ef<-t%>%select(., EF)%>% xts(., t.d)

# trends<-ts_trend(t)

noise_trend.sst<-ts_trend(noise.sst)
noise_trend.chl<-ts_trend(noise.chl)
noise_trend.ef<-ts_trend(noise.ef)

p7<-ts_ggplot(noise.chl, ts_trend(noise.chl))+scale_color_manual(values = c("darkgreen", "purple"), labels=c("Mean CHL [mg/m3/day]", "Loews Trend"))+ theme_tsbox() + ggtitle("TC noise component") 
p8<-ts_ggplot(noise.sst, ts_trend(noise.sst))+scale_color_manual(values = c("red", "purple"), labels=c("Mean SST (째C)", "Loews Trend"))+ theme_tsbox()+ ggtitle("TC noise component")
p9<-ts_ggplot(noise.ef, ts_trend(noise.ef))+scale_color_manual(values = c("black", "purple"), labels=c("Mean Export Flux (mgC/m^2/day)", "Loews Trend"))+ theme_tsbox()+ ggtitle("TC noise component")

```

#### comparing trends

```{r}

sst_trend.dif<-trend.sst-signal_trend.sst
chl_trend.dif<-trend.chl-signal_trend.chl
ef_trend.dif<-trend.ef-signal_trend.ef




# p<-ts_ggplot(t.chl, signal.chl)


```




# matching ONI index to trend

```{r}
oni<-download_oni()
oni<-oni%>% filter(Date>= min(t.chl$time), Date<=max(t.chl$time))
t.oni<-xts(oni$ONI, oni$Date)

cutoff<-'2020-08-12'
start<-min(data$signal$date)
pdo<-download_pdo()
# heat.sst<-filter(t.sst, time<=cutoff)
pdo<-pdo%>% filter(Date>= start, Date<=cutoff)
# pdo<-pdo%>%filter(Date>= min(t.chl$time), Date<=max(t.chl$time))


pdo$PDO<-scale(pdo$PDO)
t.pdo<-xts(pdo$PDO, pdo$Date)

# ccf need tim series to be smae smapling ferqucny..

t.chl$CHL<-scale(t.chl$CHL)
t.sst$SST<-scale(t.sst$SST)
t.ef$EF<-scale(t.ef$EF)

# t.pdo$value<-scale(t.pdo$value)
p13<-ts_ggplot(t.pdo,  t.chl, ts_trend(t.chl), -ts_trend(t.pdo))+ theme_tsbox() + ggtitle("CHL")

p14<-ts_ggplot(t.pdo,  t.sst, ts_trend(t.sst), -ts_trend(t.pdo))+ theme_tsbox()+ggtitle("SST")
p15<-ts_ggplot(t.pdo,  t.ef, ts_trend(t.ef), -ts_trend(t.pdo))+ theme_tsbox() + ggtitle("EF")

p16<-ts_ggplot(t.pdo,  t.chl, ts_trend(t.chl), ts_trend(t.pdo))+ theme_tsbox() + ggtitle("CHL")
p17<-ts_ggplot(t.pdo,  t.sst, ts_trend(t.sst), ts_trend(t.pdo))+ theme_tsbox()+ggtitle("SST")
p18<-ts_ggplot(t.pdo,  t.ef, ts_trend(t.ef), ts_trend(t.pdo))+ theme_tsbox() + ggtitle("EF")

trend.pdo<--1*ts_trend(t.pdo)


test<-(ts_trend(t.chl))
# test%>%ts_frequency(., to="month", aggregate = "mean")
# test1<-ts_frequency(((t) %>% filter(., id=="CHL")), to=12, aggregate = "mean")

# trend.chl<- t.chl %>%ts_frequency(., to="month", aggregate="mean") %>% ts_trend()
# cor(-ts_trend(t.pdo), ts_trend(t.chl))

par(mfrow = c(2, 1))
p13
p15


p.new<-ts_plot(t.pdo,  t.chl, ts_trend(t.chl), -ts_trend(t.pdo), title = "CHL") 
```

```{r}


p10<-ggplot()+geom_point(data=data$signal, aes(x=date, y=avg_CHL_mg_m3_day, color="Signal"))+ 
geom_point(data=data$noise, aes(x=date, y=avg_CHL_mg_m3_day, color="Noise"))+ 
geom_line(data=ts_df(trend.chl), aes(x=time, y=value, color="Trend"))+
labs(y="Mean CHL [mg/m3/day]")+
scale_color_manual(values=c(Signal="darkgreen", Noise="#640064", Trend="black"))+
theme(legend.position="bottom") +
theme(legend.title=element_blank())


# p.signal<-data$signal


p11<-ggplot()+geom_point(data=data$signal, aes(x=date, y=avg_SST_C, color="Signal"))+ 
geom_point(data=data$noise, aes(x=date, y=avg_SST_C, color="Noise"))+ 
geom_line(data=ts_df(trend.sst), aes(x=time, y=value, color="Trend"))+
xlim(min(data$signal$date), max(data$signal$date))+
ylim(20, 30)+
labs(y="Mean SST (째C)")+
scale_color_manual(values=c(Signal="red", Noise="#00ffff", Trend="black"))+
theme(legend.position="bottom") +
theme(legend.title=element_blank())



p12<-ggplot()+geom_point(data=data$signal, aes(x=date, y=avg_EF_mgC_m2_day, color="Signal"))+ 
geom_point(data=data$noise, aes(x=date, y=avg_EF_mgC_m2_day, color="Noise"))+ 
geom_line(data=ts_df(trend.ef), aes(x=time, y=value, color="Trend"))+
ylim(35, 130)+
labs(y="Mean Export Flux (mgC/m^2/day)")+
scale_color_manual(values=c(Signal="brown", Noise="#2aa5a5", Trend="black"))+
theme(legend.position="bottom") +
theme(legend.title=element_blank())


```



# plots 1
```{r}
plots<-vector(mode='list')

#time series with trends
plots[[1]]<-p1
plots[[2]]<-p2
plots[[3]]<-p3

plots




```

saving plots
```{r}

setwd(fig)
# pdf("figure_a1_v2.png", height=11 , width =8.5)
# plot_grid(plots[[1]], plots[[2]], plots[[3]], ncol=1, labels="auto")
# dev.off()



pdf("figure_a2_v3.pdf", height=11 , width =9.5)
plot_grid(p4,p7,p5,p8,p6,p9, ncol=2, labels="auto")
dev.off()


# 
# pdf("figure_a3_v2.pdf", height=11 , width =8.5)
# plot_grid(p10, p11,p12, ncol=1, labels="auto")
# dev.off()
# 
# 
# pdf("figure_a4_v2.pdf", height=11 , width =8.5)
# plot_grid(p13, p14,p15, ncol=1)
# dev.off()


```



```{r}
# p10<-ts_ggplot(signal_trend.chl, noise_trend.chl, trend.chl)+ylim(.05, .1)
# p10<-ts_plot(signal_trend.chl, noise_trend.chl, trend.chl)


pa<-ts_ggplot(signal_trend.sst)
pb<-ts_ggplot(trend.sst)
# p<-
# p<-ts_ggplot(trend.sst, noise_trend.sst)

```




### random attempts
```{r}

s<-spectrum(t.chl)
f.chl<-fft(t.chl$value)
# stuff that dpes wqorkk.

test<-t %>% model(stl = STL(value))

test<-tidy_fft(t$value)


test2<-ts_decompose(t)

test<-ts_trend(t)


test<-decompose(t)

```





### xts and ts
requres t as xts object
```{r}
# seems like ther should be an easri way..


remove(t.d)
periodicity(t$avg_SST_C)

# weekly hack

ts.sst<-ts(x1$avg_SST_C, frequency=52, start=c(2002, 07))
ts.chl<-ts(x1$avg_CHL_mg_m3_day, frequency=52, start=c(2002, 07))


d.sst<-decompose(ts.sst, type = "multiplicative")
s<-spectrum(ts, demean=T)


test<-stl(ts)

# messing asbout:
test<-stl.xts(t, s.window="periodic")

s<-spectrum(t$avg_SST_C, demean=F)

test<-fft(t)



plot(fft(t), type = "l")

test<-acf(t, demean=T)
s<-spectrum(t, demean=T)

```




## with ts whioch is  apin for 8 day observersations

```{r}
start<-min(x1$date)%>%as.POSIXct()
end<-max(x1$date)%>%as.POSIXct()

start<-c(20)

start<-min(x1$date)
end<-max(x1$date)


t<-x1%>%select(.,avg_CHL_mg_m3_day, avg_SST_C, avg_EF_mgC_m2_day ) %>% ts(.,start=start, end=end, deltat =(8/365) )

t<-x1%>%select(.,avg_EF_mgC_m2_day ) %>% ts(.,start=start, end=end, deltat =(7/365) )


t1<-decompose(t, type ="additive", filter=NULL)


```






## PDO & Enso

