---
title: "figure_4_Bud_export_flux"
author: "Brandon M. Genco"
date: "10/9/2022"
output: html_document
---

# Setup  
Packages, Directories, 

## dynamic directories

```{r setup}
rm(list=ls())
# relative directories
robj<-"r_objects"
fig<-"../../figures"
gis_data<-"../../data/gis_data"
data_d<-"../../data/2018_data"

sst_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_sst_netcdf"
chl_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_chl_netcdf"


knitr::opts_chunk$set(echo =FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## packages and working directory

Installed custom hurdat package using r markdown menu
* download  tar from archive as no longer maintained on cran repository
* https://cran.r-project.org/src/contrib/Archive/HURDAT/
+ include as git submodule instead

```{r}
wd<-getwd()

f.ipak <- function(pkg){
  # loads packages, quietly, given by a vector of package names e.g., pkg<-c("ggplot", "tidyverse")
  # will install  packages listed , and their dependencies, if needed.
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE, quiet=T, verbose = F)
  sapply(pkg, require, character.only = TRUE, quietly = FALSE, warn.conflicts=F)
}


packages<-c("sp", "rgdal",  "rgeos", "raster", "readr", "tidyverse", "lubridate",  "ggthemes",  "sf", "cmocean", "ncdf4", "RNetCDF",  "plot3D", "tidync", "devtools", "stars", "ncmeta", "maps", "oce", "data.table", "fasterize", "RStoolbox", "scales", "purrr", "HURDAT", "ggpattern")

# "HURDAT",

f.ipak(packages)
# lapply(packages, require, character.only = TRUE)
# rm(f.ipak, packages)
print(paste0("Current Working Directory is ", getwd()))

```


# Functions

```{r}
f.storms<-function(x){

start<-vector(mode="character", length=length(x))
end<-vector(mode="character", length=length(x))
pres<-vector(mode="integer", length=length(x))
key<-vector(mode="character", length=length(x))
name<-vector(mode="character", length=length(x))
wind<-vector(mode="integer", length=length(x))

for(i in 1:length(x)){
  start[[i]]<-as.character(min(x[[i]]$DateTime))
  end[[i]]<-as.character(max(x[[i]]$DateTime))
  pres[[i]]<-median(x[[i]]$Pressure)
  wind[[i]]<-median(x[[i]]$Wind)
  key[[i]]<-unique(x[[i]]$Key)
  name[[i]]<-unique(x[[i]]$Name)
  
}

x<-data.frame(key=key, name=name, start=date(start), end=date(end), pressure=pres, wind=wind)
return(x)

}
```

# loading Important objects and data sets & intial data wranglaing

## funtion variables
-from previous scripts

```{r}
setwd(wd)
setwd(robj)


load("20220201_temp_workspace.RData")
rm(m.coast, database)
```


## load basic hurdat

```{r}
setwd(wd)
setwd(robj)
# h<-get_hurdat(basin="EP")
# saveRDS(h, "hurdat.R")

h<-readRDS("hurdat.R")
h$DateTime<-with_tz(h$DateTime, tz="UTC")
```

## loading  coastal subsetting objects 
- see script "GRL_Main_Figures.Rmd"
```{r}
setwd(wd)
setwd(gis_data)
coastline<-st_read("./ne_50m_land/ne_50m_land.shp") 
# ocean<-st_read("./ne_50m_ocean/ne_50m_ocean.shp") 

cl<-st_crop(coastline, xmin=function_variables$h.lon_min, ymin=function_variables$h.lat_min, xmax=function_variables$h.lon_max, ymax=function_variables$h.lat_max)
rm(coastline)

m.coast <- ggplot()+ geom_sf(data =cl, size=0.5)+ theme(axis.title.x=element_blank(), axis.title.y=element_blank())+
  theme_bw()+ theme(text = element_text(size =12)) 

# cl<-st_crop(coastline, xmin=-170, ymin=-20, xmax=-80, ymax=40) # change here based on desired figure size
# cl<-st_crop(coastline, xmin=min(h$Lon), ymin=min(h$Lat), xmax=max(h$Lon), ymax=max(h$Lat))
# oc<-st_crop(ocean, xmin=function_variables$h.lon_min, ymin=function_variables$h.lat_min, xmax=function_variables$h.lon_max, ymax=function_variables$h.lat_max)

```

## stations and buffer

```{r}
setwd(wd)
setwd(robj)

stations_positions_list<-readRDS("OC1806A_stations_positions_list.R")

st<-stations_positions_list[[3]][4,cbind(2,3)]
st<-sf::st_as_sf(st, coords =c("longitude", "latitude"),  crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
flat<-sf::st_transform(st, "+proj=aeqd +lat_0=18.5005 +lon_0=-108.502" )

## radius in km for POC select
radii<-100000 
circle_3.5_200km<-sf::st_buffer(flat, dist=radii)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

## for selecting TC that intersect
radii<-2*radii 
circle_3.5_400km<-sf::st_buffer(flat, dist=radii)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

rm(flat, radii, st, stations_positions_list)
```

## loading POC
```{r}
setwd(wd)
setwd(robj)

data<-read_rds("vgpm_integrated_all_years_202200607.R")
x<-data$st3.5
rm(data)

window_area<-round((x$`window_area (m^2)`[1]*1e-6),0)
lab_total<-paste0("Station ", "3.5", ":", " Total Export Flux - ", window_area, " km^2 area")

x$date<-ymd(x$date)
x<-select(x, date, `mean_export_flux (mgC/m^2/day) for_window_area (total/sum_grid_area)`, `total_export_flux (mgC/day)`)
names(x)<-c("date", "avg", "ef")
x$ef<-x$ef/1000000

sst<-readRDS("st35_sst_modis.R")
z<-select(sst, date, `SST_mean (area weighted)`)
rm(sst)
names(z)<-c("date", "sst")
z$date<-ymd(z$date)

chl<-readRDS("st35_chl_modis.R")
y<-select(chl, date, 'chl_mean (area weighted)')
rm(chl)
names(y)<-c("date", "chl")
y$date<-ymd(y$date)

```

# TC slection

can problly combine 4 spearte datsets int one with factacrotial category

## spatial temporal subsetting
```{r}
bbox<-st_bbox(circle_3.5_200km)

g<-filter(h, DateTime >=date(min(x$date))-60) # save 'h' in order to adjust function variables if needed.
h.pts<- sf::st_as_sf(g, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
sf::st_crop(., c(xmin=bbox$xmin[[1]], ymin=bbox$ymin[[1]], xmax=bbox$xmax[[1]], ymax=bbox$ymax[[1]])) #subset by user defined 
rm(g, bbox)
```

## split and recombine 200 km storms

```{r}

all<-h
t<-h.pts 
st_geometry(t)<-NULL
# t$ymin<--Inf
# t$ymax<-Inf
# t$DateTime<-as.Date(t$DateTime)
t$DateTime<-as_datetime(t$DateTime)

# unique(t$Status)
 
# see:  https://www.nhc.noaa.gov/data/hurdat/hurdat2-format-atl-1851-2021.pdf
#"TS" tropical cyclone of tropical storm intensity (34-63 knots)
# "TD" Tropical cyclone of tropical depression intensity (< 34 knots)
# LO – A low that is neither a tropical cyclone, a subtropical cyclone, nor an extra tropical cyclone (of any intensity)
# DB – Disturbance (of any intensity)
# splits in individual storms to hurricanes and all else. If an individual storm was bot below and a hurricane and a hurricane in the subset it mark it as a hurricane

remove_200<-unique(t$Key)
 
h<-t%>% group_by(Key) %>% filter(any(Status== "HU"))
t<-t %>% subset(., !(Key %in% unique(h$Key)))%>% group_by(Key)

t<-group_split(t)
t<-lapply(t, as.data.frame)

h<-group_split(h)
h<-lapply(h, as.data.frame)

#standard atmospheric presures in millibars

h_200<-f.storms(h)
t_200<-f.storms(t)

```


## split and recombine 400 km storms only

```{r}
setwd(wd)
setwd(robj)

bbox<-st_bbox(circle_3.5_400km)


g<-filter(all, DateTime >=date(min(x$date))-60) # save 'h' in order to adjust function variables if needed.

h.pts<- sf::st_as_sf(g, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
sf::st_crop(., c(xmin=bbox$xmin[[1]], ymin=bbox$ymin[[1]], xmax=bbox$xmax[[1]], ymax=bbox$ymax[[1]])) #subset by user defined 

# h.pts<-st_difference(h.pts, st_combine(st_geometry(cl))) # remove all points over land
rm(g)

t<-h.pts 
st_geometry(t)<-NULL


t$DateTime<-as_datetime(t$DateTime)
all_400<-t

t<-t %>% subset(., !(Key %in% remove_200))
h<-t%>% group_by(Key) %>% filter(any(Status== "HU"))
t<-t %>% subset(., !(Key %in% unique(h$Key)))%>% group_by(Key)

all_400<-all_400 %>% group_by(Key)
all_400<-group_split(all_400)
all_400<-lapply(all_400, as.data.frame)


t<-group_split(t)
t<-lapply(t, as.data.frame)

h<-group_split(h)
h<-lapply(h, as.data.frame)

h_400<-f.storms(h)
t_400<-f.storms(t)

all_400<-f.storms(all_400)
rm(t, h, h.pts)

```


# TC mathcup with varaibles

```{r}

s<-h_200%>% group_by(key) %>% group_split(.) %>% lapply(., as.data.frame) 

t<-s[[1]]


z1<-z

  before<-p$profile_dates[p$profile_dates<=x$data$DateTime]
          after<-p$profile_dates[p$profile_dates>=x$data$DateTime]
          
          if(length(before)==0){x$prior<-NA} else {
            
            before_window<-before[which(date(before) >= date(x$data$DateTime)-function_variables$h.prior)]



# star function here

f.tc_poc-function(x,y,z){

x<-select(x, date, avg)
setDT(y)
setDT(x)
data<-x[y, on='date']
rm(x, y)
setDT(data)
setDT(z)
data<-data[z, on='date']
rm(z)

s<-s%>% group_by(key) %>% group_split(.) %>% lapply(., as.data.frame)

f.match<-funcion(data, s){
  
#dates not index
pre<-data$date[(rev(which(data$date<s$start))[1])] 
overpass<-s$start
post<-
return(data)
}

data<-lapply(data, f.match)

# here list into dataframe
return(data)

}

```

```{r}

```

