---
title: "figure_4_Bud_export_flux"
author: "Brandon M. Genco"
date: "10/9/2022"
output: html_document
---

# Setup  
Packages, Directories, 

## dynamic directories

```{r setup}
rm(list=ls())
# relative directories
robj<-"r_objects"
fig<-"../../figures"
gis_data<-"../../data/gis_data"
data_d<-"../../data/2018_data"

sst_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_sst_netcdf"
chl_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_chl_netcdf"


knitr::opts_chunk$set(echo =FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

## packages and working directory

Installed custom hurdat package using r markdown menu
* download  tar from archive as no longer maintained on cran repository
* https://cran.r-project.org/src/contrib/Archive/HURDAT/
+ include as git submodule instead

```{r}
wd<-getwd()

f.ipak <- function(pkg){
  # loads packages, quietly, given by a vector of package names e.g., pkg<-c("ggplot", "tidyverse")
  # will install  packages listed , and their dependencies, if needed.
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE, quiet=T, verbose = F)
  sapply(pkg, require, character.only = TRUE, quietly = FALSE, warn.conflicts=F)
}


packages<-c("sp", "rgdal",  "rgeos", "raster", "readr", "tidyverse", "lubridate",  "ggthemes",  "sf", "cmocean", "ncdf4", "RNetCDF",  "plot3D", "tidync", "devtools", "stars", "ncmeta", "maps", "oce", "data.table", "fasterize", "RStoolbox", "scales", "purrr",  "ggpattern", "cowplot")

# "HURDAT",

f.ipak(packages)
# lapply(packages, require, character.only = TRUE)
# rm(f.ipak, packages)
print(paste0("Current Working Directory is ", getwd()))

```


# Functions

```{r}
f.storms<-function(x){

start<-vector(mode="character", length=length(x))
end<-vector(mode="character", length=length(x))
pres<-vector(mode="integer", length=length(x))
key<-vector(mode="character", length=length(x))
name<-vector(mode="character", length=length(x))
wind<-vector(mode="integer", length=length(x))

for(i in 1:length(x)){
  start[[i]]<-as.character(min(x[[i]]$DateTime))
  end[[i]]<-as.character(max(x[[i]]$DateTime))
  pres[[i]]<-median(x[[i]]$Pressure)
  wind[[i]]<-median(x[[i]]$Wind)
  key[[i]]<-unique(x[[i]]$Key)
  name[[i]]<-unique(x[[i]]$Name)
  
}

x<-data.frame(key=key, name=name, start=date(start), end=date(end), pressure=pres, wind=wind)
return(x)

}

f.tc_poc<-function(x,y,z,s, post, pre){

  pre= pre*-1
  
# x<-select(x, date, avg)
setDT(y)
setDT(x)
data<-x[y, on='date']
# rm(x, y)
setDT(data)
setDT(z)
data<-data[z, on='date']
# rm(z)

s<-s%>% group_by(key) %>% group_split(.) %>% lapply(., as.data.frame)

ndata<-list(data, s)
names(ndata)<-c("data", "s")

# to optimized  for big data turn loop below into lapply/mapply
data<-vector(mode="list", length=length(ndata$s))

for(i in 1:length(data)){
  
x<-ndata$s[[i]]
y<-ndata$data

y$days<-y$date-x$start
y<-filter(y, days %in% pre:post)
y$name<-x$name
y$key<-x$key
y$pres<-x$pressure
y$wind<-x$wind

data[[i]]<-y
}


return(data)

}




f.anomaly<-function(c){
  m<-mean(c)
  n<-c-m
  return(n)
}

f.ind_storms<-function(x, filter){
  st_geometry(x)<-NULL
  x$DateTime<-as_datetime(x$DateTime)
  
  if(filter==TRUE) {x<-x %>% group_by(Key) %>% filter(any(Status== "HU"))} else{
    x<-x %>% group_by(Key)}
  
  
  x<-group_split(x)
  x<-lapply(x, as.data.frame)
  return(x)
  
}

f.remove_close_storms<-function(x, pre){

names(x) = unlist(lapply(x,FUN=function(x)max(x$DateTime)))
x<-x[order(as.integer(names(x)))]  
y<-vector(mode="list", length=length(x))  

for(i in 1:length(x)){
    j<-i-1
      if(j>=1) {t.dif<-as.integer(min(x[[i]]$DateTime)-max(x[[j]]$DateTime))} else {
        t.dif<-(pre*2)}
   
   if(t.dif<= pre){y[[i]]<-NULL} else {y[[i]]<-x[[i]]}
    
 y<-y[lengths(y) != 0] 
names(y)<-unlist(lapply(y,FUN=function(y) unique(y$Key)))

    
   }
return(y)
   
}

f.exclusion_list<-function(removed,allstorms){
  
  x<-names(removed)
  y<-unlist(lapply(allstorms,FUN=function(allstorms) unique(allstorms$Key)))
  include<-y[(y %in% x)]
  rm(x, y, removed)
  
  x<-f.storms(allstorms)
  
  x<-filter(x, key %in% include)
  return(x)
  
  
}

# f.funky_mean<-function(c)  


```

# loading Important objects and data sets & intial data wranglaing

## funtion variables
-from previous scripts

```{r}
setwd(wd)
setwd(robj)

load("20220201_temp_workspace.RData")
rm(m.coast, database)
```

## load basic hurdat

```{r}
setwd(wd)
setwd(robj)
# h<-get_hurdat(basin="EP")
# saveRDS(h, "hurdat.R")

h<-readRDS("hurdat.R")
h$DateTime<-with_tz(h$DateTime, tz="UTC")
```

## loading  coastal subsetting objects 
- see script "GRL_Main_Figures.Rmd"
```{r}
setwd(wd)
setwd(gis_data)
coastline<-st_read("./ne_50m_land/ne_50m_land.shp") 
# ocean<-st_read("./ne_50m_ocean/ne_50m_ocean.shp") 

cl<-st_crop(coastline, xmin=function_variables$h.lon_min, ymin=function_variables$h.lat_min, xmax=function_variables$h.lon_max, ymax=function_variables$h.lat_max)
rm(coastline)

m.coast <- ggplot()+ geom_sf(data =cl, size=0.5)+ theme(axis.title.x=element_blank(), axis.title.y=element_blank())+
  theme_bw()+ theme(text = element_text(size =12)) 

# cl<-st_crop(coastline, xmin=-170, ymin=-20, xmax=-80, ymax=40) # change here based on desired figure size
# cl<-st_crop(coastline, xmin=min(h$Lon), ymin=min(h$Lat), xmax=max(h$Lon), ymax=max(h$Lat))
# oc<-st_crop(ocean, xmin=function_variables$h.lon_min, ymin=function_variables$h.lat_min, xmax=function_variables$h.lon_max, ymax=function_variables$h.lat_max)

```

## stations and buffer

```{r}
setwd(wd)
setwd(robj)

stations_positions_list<-readRDS("OC1806A_stations_positions_list.R")

st<-stations_positions_list[[3]][4,cbind(2,3)]
st<-sf::st_as_sf(st, coords =c("longitude", "latitude"),  crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
flat<-sf::st_transform(st, "+proj=aeqd +lat_0=18.5005 +lon_0=-108.502" )

## radius in km for POC select
radii<-100000 
circle_3.5_200km<-sf::st_buffer(flat, dist=radii)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

## for selecting TC that intersect
radii<-2*radii 
circle_3.5_400km<-sf::st_buffer(flat, dist=radii)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

rm(flat, radii, st, stations_positions_list)
```

## loading POC

```{r}
setwd(wd)
setwd(robj)

data<-read_rds("vgpm_integrated_all_years_202200607.R")
x<-data$st3.5
rm(data)

window_area<-round((x$`window_area (m^2)`[1]*1e-6),0)
lab_total<-paste0("Station ", "3.5", ":", " Total Export Flux - ", window_area, " km^2 area")

x$date<-ymd(x$date)
x<-select(x, date, `mean_export_flux (mgC/m^2/day) for_window_area (total/sum_grid_area)`, `total_export_flux (mgC/day)`)
names(x)<-c("date", "avg", "ef")
x$ef<-x$ef/1000000

sst<-readRDS("st35_sst_modis.R")
z<-select(sst, date, `SST_mean (area weighted)`)
rm(sst)
names(z)<-c("date", "sst")
z$date<-ymd(z$date)

chl<-readRDS("st35_chl_modis.R")
y<-select(chl, date, 'chl_mean (area weighted)')
rm(chl)
names(y)<-c("date", "chl")
y$date<-ymd(y$date)

```

# TC slection

can problly combine 4 spearte datsets int one with factacrotial category

## spatial temporal subsetting
```{r}
all<-h


bbox<-st_bbox(circle_3.5_200km)

g<-filter(h, DateTime >=date(min(x$date))-60) # save 'h' in order to adjust function variables if needed.
h.pts_200<- sf::st_as_sf(g, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
sf::st_crop(., c(xmin=bbox$xmin[[1]], ymin=bbox$ymin[[1]], xmax=bbox$xmax[[1]], ymax=bbox$ymax[[1]])) #subset by user defined 
rm(g, bbox)

bbox<-st_bbox(circle_3.5_400km)

g<-filter(h, DateTime >=date(min(x$date))-60) # save 'h' in order to adjust function variables if needed.
h.pts_400<- sf::st_as_sf(g, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
  sf::st_crop(., c(xmin=bbox$xmin[[1]], ymin=bbox$ymin[[1]], xmax=bbox$xmax[[1]], ymax=bbox$ymax[[1]])) #subset by user defined 
rm(g, bbox)

```

## subeting for figure 4 anlysis
-400 km and 200km pts
-TCs and HU for each ass needed
-set 'pre" variabel to exclude storms that where with that number of days ahead of selected storms
- if filter = TRUE only returns hurricane status 


```{r}

# spatial and storm status

pre=35

# if filter = TRUE opnly returns hurricane status 

all_400<-f.ind_storms(h.pts_400, filter=FALSE)
all_200<-f.ind_storms(h.pts_200, filter=FALSE)
h_200<-f.ind_storms(h.pts_200, filter=TRUE)


# remove previous

all_400_remove<-f.remove_close_storms(x=all_400, pre=pre)

# finde storms to exlcude

h_200<-f.exclusion_list(removed=all_400_remove, allstorms = h_200)



# final before plotting 

```


## creat anomalies
```{r}
x$ef.a<-f.anomaly(x$ef)
x$avg.a<-f.anomaly(x$avg)

y$chl.a<-f.anomaly(y$chl)
z$sst.a<-f.anomaly(z$sst)


```

## do match up
- pick window
```{r}




data<-f.tc_poc(x,y,z, s=h_200, pre=18, post=45)
# data<-f.tc_poc(x,y,z, s=t_200, pre=18, post=60)
# data<-f.tc_poc(x,y,z, s=tc_200, pre=18, post=60)

```


# plotting

-plottinf defaults
```{r}
lab_chl<-"Chlorophyll-a [μg/L]"
lab_chl.a<-"Chlorophyll-a Anomaly [μg/L]"

lab_sst<-"SST (°C)"
lab_sst.a<-"SST Anomaly (°C)"

lab_ef<-"Total export flux (mgC/day)"
lab_ef.a<-"Total export flux Anomaly (mgC/day)"


lab_avg<-"Mean export flux (mgC/m^2/day)"
lab_avg.a<-"Mean export flux Anomaly (mgC/m^2/day)"


```


## simple plots per varible 

### with legned
```{r}



p1<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl, col=name)))+ylab(lab_chl)

p2<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl.a, col=name)))+ylab(lab_chl.a)

p3<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst, col=name)))+ylab(lab_sst)

p4<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst.a, col=name)))+ylab(lab_sst.a)

p5<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg, col=name)))+ylab(lab_avg)

p6<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg.a, col=name)))+ylab(lab_avg.a)

p7<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef, col=name)))+ylab(lab_ef)

p8<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef.a, col=name)))+ylab(lab_ef.a)


```

### without names
```{r}

p1<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl)))+ylab(lab_chl)

p2<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl.a)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl.a)))+ylab(lab_chl.a)

p3<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst)))+ylab(lab_sst)

p4<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst.a)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst.a)))+ylab(lab_sst.a)

p5<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg)))+ylab(lab_avg)

p6<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg.a)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg.a)))+ylab(lab_avg.a)

p7<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef)))+ylab(lab_ef)

p8<-ggplot()+
  lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef.a)))+
  lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef.a)))+ylab(lab_ef.a)


```

### single legend  for mutiple plots
```{r}

p1<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl, col=name)))+ylab(lab_chl)

p2<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl.a, col=name)))+ylab(lab_chl.a)

p3<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst, col=name)))+ylab(lab_sst)

p4<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst.a, col=name)))+ylab(lab_sst.a)

p5<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg, col=name)))+ylab(lab_avg)

p6<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg.a, col=name)))+ylab(lab_avg.a)

p7<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef, col=name)))+ylab(lab_ef)

p8<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef.a, col=name)))+ylab(lab_ef.a)


```

### without legends
```{r}


p1<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl, col=name)))+ylab(lab_chl)+
theme(legend.position="none")

p2<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=chl.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=chl.a, col=name)))+ylab(lab_chl.a)+
theme(legend.position="none")

p3<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst, col=name)))+ylab(lab_sst)+
theme(legend.position="none")

p4<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=sst.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=sst.a, col=name)))+ylab(lab_sst.a)+
theme(legend.position="none")

p5<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg, col=name)))+ylab(lab_avg)+
theme(legend.position="none")

p6<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=avg.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=avg.a, col=name)))+ylab(lab_avg.a)+
theme(legend.position="none")

p7<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef, col=name)))+ylab(lab_ef)+
theme(legend.position="none")

p8<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef.a, col=name)))+ylab(lab_ef.a)+
theme(legend.position="none")



pl<-ggplot()+
lapply(data, function(z) geom_point(data = z, aes(x=days, y=ef.a, col=name)))+
lapply(data, function(z) geom_line(data = z, aes(x=days, y=ef.a, col=name)))+ylab(lab_ef.a)



legend <- get_legend(pl)



```



# saving_plots
## single legend
```{r}
setwd(wd)
setwd(fig)
# 
# p<-plot_grid(p1,p2,p3,p4,p5,p6,p7,p8, ncol=2)
# pdf("test.pdf", height=11 , width =8.5)
# plot_grid(p, NULL, legend, ncol=3, rel_widths = c(10,.1,1.5))
# dev.off()

ptest<-plot_grid(p1, p7, ncol=2)
pdf("test2.pdf", width=11 , height=6)
plot_grid(ptest, NULL, legend, ncol=3, rel_widths = c(10,.1,1.5))
dev.off()


# plot_grid(p, NULL, legend, ncol=3, rel_widths = c(10,.1,1.5))

```

## simple
```{r}
setwd(wd)
setwd(fig)

pdf("test.pdf", height=11 , width =8.5)
plot_grid(p1,p2,p3,p4,p5,p6,p7,p8, ncol=1)
dev.off()



```



