---
title: "figure2_new"
author: "Brandon M. Genco"
date: "10/3/2022"
output: html_document
---

# Packages, Directories

## dynamic directories

```{r setup}
rm(list=ls())
# relative directories
r_scriptwd<-getwd()
wd<-substring(r_scriptwd,1,nchar(r_scriptwd) -10) # hardcoding replace here
knitr::opts_knit$set(root.dir = wd)

robj<-"r_objects"
fig<-"../../figures"
gis_data<-"../../data/gis_data"
data_d<-"../../data/2018_data"
# data_d<-"../../data"
ocean_color<-"../../data/ocean_color_bud"
bathy_d<-"../../data/bathy" # edit this


# old NC files
aqua_directory<-"../../data/ocean_color_bud/aqua"
terra_directory<-"../../data/ocean_color_bud/terra"
# viirs_directory<-"../../data/ocean_color_bud/terra" this might have been worng for figures

viirs_directory<-"../../data/ocean_color_bud/viirs"

#absolute directory
drop_img<-"/home/brandon/Dropbox/MERCED/dissertation/presentations/images"

knitr::opts_chunk$set(echo =FALSE)
#knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # looks forr project file. None on Callisto
```

## Load Packages
* Change 'packages' vector accordingly
* change font type
* to do trim uneeded package

```{r}
# wd<-getwd()
f.ipak <- function(pkg){
  
  # loads packages, quietly, given by a vector of package names e.g., pkg<-c("ggplot", "tidyverse")
  # will install  packages listed , and their dependencies, if needed.
  
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE, quiet=T, verbose = F)
  sapply(pkg, require, character.only = TRUE, quietly = FALSE, warn.conflicts=F)
}
packages<-c("stars", "gridExtra", "cowplot", "sf", "ggspatial","stringr","sp", "raster","readr" ,"tidyverse", "ggplot2", "lubridate",  "ggthemes", "data.table", "reshape2", "patchwork", "RColorBrewer", "marmap", "extrafont", "oce", "ncdf4", "raster", "RStoolbox", "cmocean", "metR",  "ggimage", "scales", "gtable")  # set packages here


# " grImport2"
# newer ubuntu 24. does not have "rgdal",  "rgeos", - so removed will need to see if this breaks other scripts or if sf and terra are all I need


f.ipak(packages)
rm(packages, f.ipak)
print(paste0("Current Working Directory is ", getwd()))

```

# data

## aqau, terra, viirs combined
* produces combination of aqau and terra chla
* change directory by computer, improve here
```{r}

#### combining aqau terra, and viirs ####

f.tmp1<-function(x){
  y<-nc_open(x)
  chl<-ncvar_get(y, 'chlor_a')
  lon<-ncvar_get(y, 'lon')
  lat<-ncvar_get(y, 'lat')
  rownames(chl)<-lon
  colnames(chl)<-lat
  nc_close(y)
  rm(y)
  x<-chl
  return(x)
}
f.tmp2<-function(x){
  y<-nc_open(x)

  
  end<-ncatt_get(y, attname = 'time_coverage_end', varid = 0, verbose=F)
  end<-end$value
  end<-ymd_hms(end)
  # end<-with_tz(end, tz="US/Mountain") The 'US/Mountain' format is deprecated in newer versions of the time zone database that lubridate uses.
  end<-with_tz(end, tzone = "America/Denver")
  
  # time<-c(start, end, (end-start))
  day<-day(end)
  nc_close(y)
  # rm(y, start, end)
  rm(y, end)
  
  return(as.character(day))
  
  
  lon<-ncvar_get(y, 'lon')
  lat<-ncvar_get(y, 'lat')
  rownames(chl)<-lon
  colnames(chl)<-lat
  nc_close(y)
  rm(y)
  x<-chl
  return(x)
}

# aqua 
directory<-aqua_directory
setwd(wd)
setwd(directory)
files<-list.files()

a<-lapply(files, f.tmp1)
dates<-lapply(files, f.tmp2)
names(a)<-as.character(dates)
rm(files, directory, dates)

#terra
directory<-terra_directory
setwd(wd)
setwd(directory)
files<-list.files()

t<-lapply(files, f.tmp1)
dates<-lapply(files, f.tmp2)
names(t)<-as.character(dates)
rm(files, directory, dates)

lon<-as.numeric(rownames(a[[1]]))
lat<-as.numeric(colnames(a[[1]]))


#viirs
setwd(wd)
directory<-viirs_directory
setwd(directory)
files<-list.files()

v<-lapply(files, f.tmp1)
dates<-lapply(files, f.tmp2)
names(v)<-as.character(dates)
rm(files, directory, dates)


combined<-vector(mode="list", length=length(a))
for(i in 1:length(combined)){
combined[[i]]<-(a[[i]]+t[[i]]+v[[i]])/3
  }

for(i in 1:length(combined)){
  combined[[i]]<-ifelse(is.na(combined[[i]]),(a[[i]]+t[[i]])/2,combined[[i]])
}

for(i in 1:length(combined)){
  combined[[i]]<-ifelse(is.na(combined[[i]]),(a[[i]]+v[[i]])/2,combined[[i]])
}

for(i in 1:length(combined)){
  combined[[i]]<-ifelse(is.na(combined[[i]]),(t[[i]]+v[[i]])/2,combined[[i]])
}

for(i in 1:length(combined)){
  combined[[i]]<-ifelse(is.na(combined[[i]]),a[[i]],combined[[i]])
}

for(i in 1:length(combined)){
  combined[[i]]<-ifelse(is.na(combined[[i]]),t[[i]],combined[[i]])
}

for(i in 1:length(combined)){
  combined[[i]]<-ifelse(is.na(combined[[i]]),v[[i]],combined[[i]])
}

names(combined)<-names(a)
rm(a,t,v, i)
rm(f.tmp1, f.tmp2)
```

## geotiif objects 
 load list
commnetd out - make ggplot objects

* redo for new figures:
* even versu odd, can I slecte by date?
* IMPORTANT raster stack is a local directory pointer object 
```{r}

# directory<-paste(ocean_color, "/true_color/viirs", sep ="") #change to modis if nessecary 
setwd(wd)
setwd(ocean_color)
setwd("./true_color/viirs")
files<-list.files()

v_rgb<-lapply(files,stack)
#v_rgb<-lapply(v_rgb, ggRGB, r=1, g=2, b=3) 
rm(files)
```



## staion 3.5 circle
* add 200 km circle- 100km radi
https://stackoverflow.com/questions/34183049/plot-circle-with-a-certain-radius-around-point-on-a-map-in-ggplot2

```{r}
setwd(wd)
setwd(robj)


stations_positions_list<-readRDS("OC1806A_stations_positions_list.R")
st3.5<-stations_positions_list[[3]][4,cbind(2,3)]
rm(stations_positions_list)

st3.5<-sf::st_as_sf(st3.5, coords =c("longitude", "latitude"),  crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
flat<-sf::st_transform(st3.5, "+proj=aeqd +lat_0=18.5005 +lon_0=-108.502" )
circle<-sf::st_buffer(flat, dist=100000)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") 
rm(flat, st3.5)


```

## eye positon Bud & Aletta
- custom csv
- edited for custom image of hurricane over Bud

```{r}

setwd(wd)
setwd(gis_data)
directory<-getwd()

eyes<-read_csv("aletta_bud_eye_position_visual.csv")


a<-filter(eyes, storm=="Aletta")  %>% st_as_sf(., coords=c("lon", "lat"))
st_crs(a)<-"+proj=longlat +datum=WGS84 +no_defs"

b<-filter(eyes, storm=="Bud")

b<-data.frame(day=b$day, lon=b$lon, lat=b$lat, image=paste0(directory, "/hurricane.png"))
b<-b%>% st_as_sf(., coords=c("lon", "lat"))

st_crs(b)<-"+proj=longlat +datum=WGS84 +no_defs"


```

# figure
## Functions

### plot functions
```{r}
f.fig2<-function(combined, v_rgb, i, t, l){
  t1<-combined[[i]]
  t2<-v_rgb[[i]]
  date<-paste0("June", " ", names(combined)[i])

  eye.a<-filter(a, day==as.numeric(names(combined[i])))%>% select(., geometry)
  # eye.b<-filter(a, day==as.numeric(names(combined[i]))) %>% select(., geometry)
  eye.b<-filter(b, day==as.numeric(names(combined[i]))) 

  lat<-as.numeric(row.names(t(t1)))
  lon<-as.numeric(colnames(t(t1)))
  
  t1<-raster(t(t1))

  extent(t1)<-extent(min(lon), max(lon), min(lat), max(lat))
  # extent(t1)<-extent(-120, -100, 10, 33.5)
  
  
  t1_ex<-extent(t1)
  t2_ex<-extent(t2)
  extent(t1)<-extent(t1_ex[1], t2_ex[2], t2_ex[3], t2_ex[4])
  extent(t2)<-extent(t1_ex[1], t2_ex[2], t2_ex[3], t2_ex[4])
  rm(t1_ex, t2_ex)
  
  
  t3<-resample(t1, t2)
  t3<-na.omit(t3)
  
  
  # new extent
  e<-extent(t1)
  h<-abs(e[4]-e[3])
  w<-abs(e[1]-e[2])

  left<-right -(w*zoom)
  top<-(h*zoom)+bottom
  new<-as(extent(left, right, bottom, top), 'SpatialPolygons') 
  crs(new)<-"+proj=longlat +datum=WGS84 +no_defs"
  
  t2<-crop(t2, new)
  t3<-crop(t3, new)
  
  st_crs(eye.b)<-st_crs(t3)
  # eye.b<-data.frame(lon=st_geometry(eye.b)[[1]][[1]], lat=st_geometry(eye.b)[[1]][[2]], image=eye.b$image)
  
  rm(t1)
  
  f1<- ggRGB(t2, r=1, g=2, b=3, ggObj = T) + ggtitle(date)+theme_bw() +
    theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.line = element_line(colour = "black"),
          plot.margin = unit(c(t, 0, 0, l), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          #panel.background = element_rect(colour = "black", fill=NA, size=5),
          axis.title.x=element_blank(),
          axis.title.y=element_blank()) +
          scale_y_continuous(expand = c(0, 0), breaks=lat_ticks)+
          scale_x_continuous(expand = c(0, 0), breaks=lon_ticks)
          

    
if (length(eye.b$geometry)>0) {
  
  eye.b<-data.frame(lon=st_geometry(eye.b)[[1]][[1]], lat=st_geometry(eye.b)[[1]][[2]], image=eye.b$image)
  
  f3<-f1+ggR(t3, geom_raster = TRUE, ggLayer=T) +
    theme(axis.line = element_line(colour = "black"),
          plot.margin = unit(c(t, 0, 0, 0, l), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(colour = "black", fill=NA, size=5),
          axis.title.x=element_blank(),
          axis.title.y=element_blank()) +
    scale_fill_gradientn(colors = custom_color, values=cuts, na.value=NA,limits=c(0,5), 
                         name=waiver(),breaks=labs)+
    guides(fill=guide_colourbar(title=bquote(title_two), barheight = 8)) +
    theme(legend.title =element_text(size=8), legend.text=element_text(size=6)) + 
    theme(text=element_text(family="Helvetica")) + theme(legend.position = "none") +
    # geom_sf(data = circle, color = circle_color, alpha = 0, inherit.aes = FALSE)+
    circle_geom+
    geom_sf(data=eye.a, inherit.aes = FALSE, shape =aletta_symbol, col=aletta_color,  fill=aletta_color, size=aletta_size)+
    # geom_image(aes(x=lon, y=lat, image=image), data=eye.b, inherit.aes = FALSE, col=bud_color, size=bud_size,  by="width")+
    geom_image(aes(x=lon, y=lat, image=image), data=eye.b, inherit.aes = FALSE)+
    scale_size_identity()+
    coord_sf(xlim = c(left,right), ylim = c(bottom, top))
  
} else {
   f3<-f1+ggR(t3, geom_raster = TRUE, ggLayer=T) +
    theme(axis.line = element_line(colour = "black"),
          plot.margin = unit(c(t, 0, 0, 0, l), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(colour = "black", fill=NA, size=5),
          axis.title.x=element_blank(),
          axis.title.y=element_blank()) +
    scale_fill_gradientn(colors = custom_color, values=cuts, na.value=NA,limits=c(0,5), 
                         name=waiver(),breaks=labs)+
    guides(fill=guide_colourbar(title=bquote(title_two), barheight = 8)) +
    theme(legend.title =element_text(size=8), legend.text=element_text(size=6)) + 
    theme(text=element_text(family="Helvetica")) + theme(legend.position = "none") +
    # geom_sf(data = circle, color = circle_color, alpha = 0, inherit.aes = FALSE)+
    circle_geom+
    geom_sf(data=eye.a, inherit.aes = FALSE, shape =aletta_symbol, col=aletta_color,  fill=aletta_color, size=aletta_size)+
    coord_sf(xlim = c(left,right), ylim = c(bottom, top))
  
  }
  
  

  
  return(f3)
}
f.fig2_no_y<-function(combined, v_rgb, i, t, l){
  t1<-combined[[i]]
  t2<-v_rgb[[i]]
  date<-paste0("June", " ", names(combined)[i])
  
  eye.a<-filter(a, day==as.numeric(names(combined[i]))) %>% select(., geometry)
  # eye.b<-filter(a, day==as.numeric(names(combined[i]))) %>% select(., geometry)
  eye.b<-filter(b, day==as.numeric(names(combined[i]))) 

  
  lat<-as.numeric(row.names(t(t1)))
  lon<-as.numeric(colnames(t(t1)))
  
  t1<-raster(t(t1))
  extent(t1)<-extent(min(lon), max(lon), min(lat), max(lat))
  # extent(t1)<-extent(-120, -100, 10, 33.5)
  
  t1_ex<-extent(t1)
  t2_ex<-extent(t2)
  extent(t1)<-extent(t1_ex[1], t2_ex[2], t2_ex[3], t2_ex[4])
  extent(t2)<-extent(t1_ex[1], t2_ex[2], t2_ex[3], t2_ex[4])
  rm(t1_ex, t2_ex)
  
  
  t3<-resample(t1, t2)
  t3<-na.omit(t3)
 
  # new extent
  e<-extent(t1)
  h<-abs(e[4]-e[3])
  w<-abs(e[1]-e[2])

  left<-right -(w*zoom)
  top<-(h*zoom)+bottom
  new<-as(extent(left, right, bottom, top), 'SpatialPolygons') 
  crs(new)<-"+proj=longlat +datum=WGS84 +no_defs"
  
  t2<-crop(t2, new)
  t3<-crop(t3, new)
  
  st_crs(eye.b)<-st_crs(t3)
  # eye.b<-data.frame(lon=st_geometry(eye.b)[[1]][[1]], lat=st_geometry(eye.b)[[1]][[2]], image=eye.b$image)
  

  rm(t1)
  
  f1<- ggRGB(t2, r=1, g=2, b=3, ggObj = T) + ggtitle(date)+theme_bw() +
    theme(plot.title = element_text(hjust = 0.5))+
    theme(axis.line = element_line(colour = "black"),
          plot.margin = unit(c(t, 0, 0, l), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          #panel.background = element_rect(colour = "black", fill=NA, size=5),
          axis.title.x=element_blank(),
          axis.title.y=element_blank()) +
          scale_y_continuous(expand = c(0, 0), breaks=lat_ticks)+
          scale_x_continuous(expand = c(0, 0), breaks=lon_ticks)
          
 
  if (length(eye.b$geometry)>0) {
   
  eye.b<-data.frame(lon=st_geometry(eye.b)[[1]][[1]], lat=st_geometry(eye.b)[[1]][[2]], image=eye.b$image) 
   
  f3<-f1+ggR(t3, geom_raster = TRUE, ggLayer=T) +
    theme(axis.line = element_line(colour = "black"),
          plot.margin = unit(c(t, 0, 0, 0, l), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(colour = "black", fill=NA, size=5),
          axis.title.x=element_blank(),
          axis.title.y=element_blank()) +
    scale_fill_gradientn(colors = custom_color, values=cuts, na.value=NA,limits=c(0,5), 
                         name=waiver(),breaks=labs)+
    guides(fill=guide_colourbar(title=bquote(title_two), barheight = 8)) +
    theme(legend.title =element_text(size=8), legend.text=element_text(size=6)) + 
    theme(text=element_text(family="Helvetica")) + theme(legend.position = "none") +
    theme(axis.text.y=element_blank(), axis.ticks.y=element_blank())+
    # geom_sf(data = circle, color = circle_color, alpha = 0, inherit.aes = FALSE)+
    circle_geom+
    geom_sf(data=eye.a, inherit.aes = FALSE, shape =aletta_symbol, col=aletta_color,  fill=aletta_color, size=aletta_size)+
    # geom_image(aes(x=lon, y=lat, image=image), data=eye.b, inherit.aes = FALSE, col=bud_color, size=bud_size, by="width")+
    geom_image(aes(x=lon, y=lat, image=image), data=eye.b, inherit.aes = FALSE)+
    scale_size_identity()+
    coord_sf(xlim = c(left,right), ylim = c(bottom, top))
    
} else {
   f3<-f1+ggR(t3, geom_raster = TRUE, ggLayer=T) +
    theme(axis.line = element_line(colour = "black"),
          plot.margin = unit(c(t, 0, 0, 0, l), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(colour = "black", fill=NA, size=5),
          axis.title.x=element_blank(),
          axis.title.y=element_blank()) +
    scale_fill_gradientn(colors = custom_color, values=cuts, na.value=NA,limits=c(0,5), 
                         name=waiver(),breaks=labs)+
    guides(fill=guide_colourbar(title=bquote(title_two), barheight = 8)) +
    theme(legend.title =element_text(size=8), legend.text=element_text(size=6)) + 
    theme(text=element_text(family="Helvetica")) + theme(legend.position = "none") +
    theme(axis.text.y=element_blank(), axis.ticks.y=element_blank())+
    # geom_sf(data = circle, color = circle_color, alpha = 0, inherit.aes = FALSE)+
    circle_geom+
    geom_sf(data=eye.a, inherit.aes = FALSE, shape =aletta_symbol, col=aletta_color, fill=aletta_color, size=aletta_size)+
    coord_sf(xlim = c(left,right), ylim = c(bottom, top))
  }

        
  
  return(f3)
}
```

### legends
```{r}
f.fig2_legend<-function(combined, v_rgb, height, width, t,b,r,l, title.textsize, marks.textsize){
  t1<-combined[[1]]
  t2<-v_rgb[[1]]
  
  lat<-as.numeric(row.names(t(t1)))
  lon<-as.numeric(colnames(t(t1)))
  
  t1<-raster(t(t1))
  extent(t1)<-extent(min(lon), max(lon), min(lat), max(lat))
  # extent(t1)<-extent(-120, -100, 10, 33.5)
  
  t1_ex<-extent(t1)
  t2_ex<-extent(t2)
  extent(t1)<-extent(t1_ex[1], t2_ex[2], t2_ex[3], t2_ex[4])
  extent(t2)<-extent(t1_ex[1], t2_ex[2], t2_ex[3], t2_ex[4])
  rm(t1_ex, t2_ex)
  
  
  t3<-resample(t1, t2)
  t3<-na.omit(t3)
  
  # new extent
  e<-extent(t1)
  h<-abs(e[4]-e[3])
  w<-abs(e[1]-e[2])

  left<-right -(w*zoom)
  top<-(h*zoom)+bottom
  
  new<-as(extent(left, right, bottom, top), 'SpatialPolygons') 
  crs(new)<-"+proj=longlat +datum=WGS84 +no_defs"
  
  t3<-crop(t3, new)
  
  rm(t1)

  
  p<-ggplot()+ggR(t3, geom_raster = TRUE, ggLayer=T) +
    theme(axis.line = element_line(colour = "black"),
          plot.margin = unit(c(0, 0, 0, 0, 0), "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(colour = "black", fill=NA, size=5),
          axis.title.x=element_blank(),
          axis.title.y=element_blank()) +
    scale_fill_gradientn(colors = custom_color, values=cuts, na.value=NA,limits=c(0,5), 
                         name=waiver(),breaks=labs)+
    guides(fill=guide_colourbar(title=title_two, barheight = height, barwidth = width)) +
    theme(legend.title =element_text(size=title.textsize), legend.text=element_text(size=marks.textsize)) + 
    theme(text=element_text(family="Helvetica"))
    # xlim(left, right) +ylim(bottom,top)
  
  legend <- get_legend(p + theme(legend.box.margin = margin(t, r, b, l)))
  rm(p, t3, t2) 
  return(legend)
  
} # l = legend margin left, b=barhieght (in cm ) of legend
# 
# f.fig2_legend_eyes<-function(offset_1, x_space, plot_x, plot_y, text_size){
# 
#   circle_size<-x_space
#   
#   x1<-round((offset_1 * plot_x), 1)
#   x_equal<-(plot_x-x1)/3
#   x2<-x1+x_space
#   x3<-x1+x_equal
#   x4<-x3+x_space
#   x5<-x3+x_equal
#   x6<-x5+(x_space *3)
#   y1<-plot_y/2
#   
#   new_eye.b<-data.frame(x=x1, y=y1, image=b$image) 
#   new_eye.a<-data.frame(x=x3, y=y1)%>%st_as_sf(., coords=c("x", "y"))
#   center<-c((x5+circle_size), y1)
#   circle<-st_point(x=, center, dim="XY")%>%sf::st_buffer(., dist=circle_size)
#   empty<-data.frame(x=c(0, 0, plot_x, plot_x), y=c(c(plot_y, 0, plot_y, 0)))
#   
# text1<-"TC Bud Eye"
# text2<-"TC Aletta Eye"
#  # text3<-"Station 3.5 - 100km radius"
#   
#  
#  text3<-"200km Diameter\nStation 3.5 "
# 
#    
#  p<-ggplot()+
#     geom_sf(data = circle, color = circle_color, alpha = 0)+
#     geom_sf(data=new_eye.a, shape =aletta_symbol, col=aletta_color,  fill=aletta_color, size=aletta_size)+
#     # circle_geom+
#     geom_image(data=new_eye.b, aes(x, y, image = image), asp = 10)+ scale_size_identity()+
#     annotate("text", x=x2, y=y1, label= text1, hjust = 0)+
#     annotate("text", x=x4, y=y1, label= text2, hjust = 0)+
#     annotate("text", x=x6, y=y1, label= text3, hjust = 0)+
#     theme(text = element_text(size = text_size))+   
#     theme_void()+
#     coord_sf(xlim = c(0,plot_x), ylim = c(0, plot_y))
#   
#  # np<-p+coord_flip(ylim=c(0, plot_y))
#  # rm(p)
#  return(p)
#  
# 
#  } #as of now does not work with circle_geom adddtion

```

## figure 2 and s5

select dates
 - zoomed in main figure. dates:
 4,   5, 9
 10, 11, 12
 14, 15, 16
 17, 21 ,23
 
-supplement fulkl resolution
 
6    7  8
13, 18, 19
20  22  24
25  26  27

 
```{r}

#Much of this should really be compressed into  a function...

start<-Sys.time()
rm(p, s.p)
# changing files will likely break folowin index
# plotting parameters

options(warn=-1)
plots<-vector(mode='list', length = length(combined))

# cuts<-c(0, 0.01, 0.02, 0.04,  0.08,  0.1,  0.15, 0.2, 0.35, 0.5, 0.8, 0.9, 1, 2,3,4, 5)
# Refined breaks for better differentiation across the range les emphais an low avlues
cuts <- c(0, 0.05, 0.1, 0.15, 0.2, 0.3, 0.4, 0.5, 0.7, 0.9, 1.2, 1.5, 2.0, 2.5, 3.0, 4.0, 5.0)
n <- length(cuts) + 1
custom_color <- oce::oceColorsViridis(n)
cuts <- rescale(cuts)
n<-length(cuts)+1
custom_color<-oce::oceColorsViridis(n)

# custom_color<-rev(rainbow(n))

cuts<-rescale(cuts)
title_two<-expression(atop(textstyle("Chl a"), textstyle("mg m"^-3*"")))
labs<-c(0.1, .5, 1, 2 , 2.5, 5)
# bar_height<-25
bar_height<-22.70

# plotting colors & symbols + size
# "#FF7700", "#E67300", "#CD8500

# complimentry: "#E65832"


circle_color1<-"white"
circle_color2<-"#E65832"
base<-5.0
outline<-1.5*base
line1<-"solid"
line2<-"dashed"

circle_parameters <- c(
  circle_color1 = circle_color1,  
  circle_color2 = circle_color2,
  base = base,
  outline = outline,
  line1 = line1,
  line2 = line2
)

circle_geom <- list(
  geom_sf(data = circle, color = circle_color1, linetype = line1, size = outline, alpha = 0, inherit.aes = FALSE),
  geom_sf(data = circle, color = circle_color2, linetype = line2, size = base, alpha = 0, inherit.aes = FALSE)
)

# circle_geom<-circle_geom[[2]]

# bud_color<-"#377eb8"
# aletta_color<-"#4daf4a"

bud_color<-"black"
# aletta_color<-"midnightblue"
aletta_color<-"black"
aletta_size<-2
bud_size<-4

# bud_symbol<-13
# aletta_symbol<-12

bud_symbol<-NULL
aletta_symbol<-25

lat_ticks<-seq(15,30, b=5)
lon_ticks<-c(-115, -110, -105)
 
# image extent
# combinded full:
# class      : Extent 
# xmin       : -122.4792 
# xmax       : -97.02084 
# ymin       : 5.520833 
# ymax       : 32.97917 


right<--104.7671
right<--100.8555
# shfit right to get Aletta

right<--101.8555

# bottom<-11.55
bottom<-12.5
# zoom<-.75
# right<--97.02084
# bottom<-5.520833

zoom<-.60
# zoom<-1

### Main figure select days ####

i<-which(names(combined)==4)
plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==10)
plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==14)
plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==17)
plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==5)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==9)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==11)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==12)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==15)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==16)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==21)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
i<-which(names(combined)==23)
plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)


p<-(plots[[which(names(combined)==4)]]+ plots[[which(names(combined)==5)]]+plots[[which(names(combined)==9)]]+plots[[which(names(combined)==10)]]+plots[[which(names(combined)==11)]]+ plots[[which(names(combined)==12)]]+ plots[[which(names(combined)==14)]]+ plots[[which(names(combined)==15)]]+plots[[which(names(combined)==16)]]+plots[[which(names(combined)==17)]]+ plots[[which(names(combined)==21)]]+plots[[which(names(combined)==23)]]+plot_layout(ncol=3))

# legend<-f.fig2_legend(combined, v_rgb, height=bar_height, width=1, t=-390, b=0, r=0, l=-115,  title.textsize=10, marks.textsize=8)


### supplements  ####

# right<--97.02084
# bottom<-5.520833
# 
# zoom<-1
# lat_ticks<-seq(10,30, b=5)
# lon_ticks<-seq(-120, -100, b=10)
# 
# 
# i<-which(names(combined)==6)
# plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==13)
# plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==20)
# plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==25)
# plots[[i]]<-f.fig2(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==7)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==8)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==18)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==19)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==22)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==24)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==26)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# i<-which(names(combined)==27)
# plots[[i]]<-f.fig2_no_y(combined, v_rgb, i=i, t=0, l=0)
# 
# s.p<-(plots[[which(names(combined)==6)]]+ plots[[which(names(combined)==7)]]+plots[[which(names(combined)==8)]]+plots[[which(names(combined)==13)]]+plots[[which(names(combined)==18)]]+ plots[[which(names(combined)==19)]]+ plots[[which(names(combined)==20)]]+ plots[[which(names(combined)==22)]]+plots[[which(names(combined)==24)]]+plots[[which(names(combined)==25)]]+ plots[[which(names(combined)==26)]]+plots[[which(names(combined)==27)]]+plot_layout(ncol=3))
rm(plots)


# legend.sup<-f.fig2_legend(combined, v_rgb, height=bar_height, width=1, t=-390, b=0, r=0, l=-115,  title.textsize=10, marks.textsize=8)

## supplementray figure

end<-Sys.time()
elapsed<-end-start
print(elapsed)

# rm( left, top,  labs, lat, lon, circle_color, custom_color, aletta_color, aletta_symbol, bud_color, bud_symbol, lat_ticks, lon_ticks, i, cuts, elapsed, start, end, zoom, title_two, n, t1, t2, t2, t1_ex, t2_ex, eye.a, eye.b)

# rm(right, left, top, bottom, labs, lat, lon, circle_color, custom_color, aletta_color, aletta_symbol, bud_color, bud_symbol, lat_ticks, lon_ticks, i, cuts, elapsed, start, end, zoom, title_two, n, t1, t2, t2, t1_ex, t2_ex, eye.a, eye.b)


# t

gc()

```


# new attempt

1) update 2nd legend with circle_geom

then:
Save two separate PDFs:

First PDF: Your original main figure with the color legend (exactly as you have it now)
Second PDF: A properly sized eye legend on a mostly blank/transparent background, with the same dimensions as the main figure


Then use a terminal command from within RStudio to combine these PDFs

#
## legends main figure

### main
```{r}

# original figure 2 lengend
t <- -390
legend <- f.fig2_legend(combined, v_rgb, height=bar_height, width=1, t=t, b=0, r=0, l=-115,
                       title.textsize=10, marks.textsize=8)

```

This first code block defines all the functions needed for creating duplicate structure PDFs:

```{r define_functions}
# newe function that replaces "f.run_duplicate_structure_test()" for creating final figure



# Function to create an overlay with duplicate structure that preserves axis text
f.create_duplicate_structure_overlay <- function(
  plot_obj, 
  legend_obj, 
  rel_widths = c(14, 1),
  legend_xmin = NULL,  # Will be calculated if NULL
  legend_xmax = 1,
  legend_ymin = 0,
  legend_ymax = 0.25,
  preserve_axis_text = TRUE,  # New parameter to control axis text preservation
  create_diagnostic = FALSE
) {
  # Helper function for null values
  "%||%" <- function(x, y) {
    if (is.null(x)) y else x
  }
  
  # Calculate legend_xmin if not provided
  legend_xmin <- legend_xmin %||% (1 - (rel_widths[2] / sum(rel_widths)))
  
  # Create a version of the main/supplement plot
  # Selectively make elements transparent, potentially preserving axis text
  invisible_plot <- plot_obj + 
    theme(
      panel.background = element_rect(fill = NA, color = NA),
      plot.background = element_rect(fill = NA, color = NA),
      panel.grid = element_blank(),
      # Conditionally preserve axis text
      axis.text = if (preserve_axis_text) element_text() else element_text(color = NA),
      axis.title = element_text(color = NA),
      axis.ticks = if (preserve_axis_text) element_line() else element_line(color = NA),
      legend.position = "none",
      plot.margin = margin(0, 0, 0, 0)
    )
  
  # Create an empty placeholder for the top of the right column
  # This is where the original color legend would be
  empty_legend_top <- ggplot() + 
    theme_void() +
    theme(
      panel.background = element_rect(fill = NA, color = NA),
      plot.background = element_rect(fill = NA, color = NA)
    )
  
  # Create the main structure with invisible plot and empty top legend
  overlay_structure <- plot_grid(
    invisible_plot, 
    empty_legend_top,
    ncol = 2, 
    rel_widths = rel_widths, 
    align = "h"
  )
  
  # If diagnostic mode is requested, create a grid overlay instead
  if (create_diagnostic) {
    # Create a grid overlay to visualize coordinate space
    grid_plot <- ggplot() +
      # Add vertical lines at 0.1 intervals
      geom_vline(xintercept = seq(0, 1, by = 0.1), color = "blue", alpha = 0.5) +
      # Add horizontal lines at 0.1 intervals
      geom_hline(yintercept = seq(0, 1, by = 0.1), color = "red", alpha = 0.5) +
      # Add text labels for coordinates
      annotate("text", x = seq(0, 1, by = 0.1), y = 0.02, 
               label = paste0(seq(0, 1, by = 0.1)), 
               color = "blue", angle = 90, hjust = 0) +
      annotate("text", x = 0.02, y = seq(0, 1, by = 0.1), 
               label = paste0(seq(0, 1, by = 0.1)), 
               color = "red", hjust = 0) +
      # Highlight the legend position rectangle
      annotate("rect", 
               xmin = legend_xmin, xmax = legend_xmax,
               ymin = legend_ymin, ymax = legend_ymax,
               alpha = 0.2, fill = "green") +
      # Add a note about the highlighted area
      annotate("text", x = (legend_xmin + legend_xmax)/2, y = (legend_ymin + legend_ymax)/2,
               label = "Legend\nPosition", color = "darkgreen") +
      # Clean theme with labels
      theme_minimal() +
      labs(title = "Coordinate Grid Overlay",
           subtitle = paste0("Legend position: xmin=", legend_xmin, 
                            ", xmax=", legend_xmax,
                            ", ymin=", legend_ymin,
                            ", ymax=", legend_ymax))
    
    # Create a version of the overlay with grid lines for diagnostic purposes
    diagnostic_overlay <- overlay_structure + 
      annotation_custom(
        grob = ggplotGrob(grid_plot),
        xmin = 0, xmax = 1, ymin = 0, ymax = 1
      )
    
    return(diagnostic_overlay)
  }
  
  # Add the legend at the specified position
  final_overlay <- overlay_structure + 
    annotation_custom(
      grob = legend_obj,  # Use provided legend object
      xmin = legend_xmin,
      xmax = legend_xmax,
      ymin = legend_ymin,
      ymax = legend_ymax
    )
  
  return(final_overlay)
}

# Function to save PDFs with duplicate structure
f.save_duplicate_structure_pdfs <- function(
  plot_obj,
  legend_obj,
  plot_type = "main",
  main_pdf_name = NULL,
  overlay_pdf_name = NULL,
  combined_pdf_name = NULL,
  main_width = 8.5,
  main_height = 11,
  rel_widths = c(14, 1),
  legend_xmin = NULL,
  legend_xmax = 1,
  legend_ymin = 0,
  legend_ymax = 0.25,
  preserve_axis_text = TRUE,  # Added parameter for axis text preservation
  create_diagnostic = FALSE
) {
  # Helper function for null values
  "%||%" <- function(x, y) {
    if (is.null(x)) y else x
  }
  
  # Set default filenames based on plot_type
  main_pdf_name <- main_pdf_name %||% paste0("figure_", plot_type, "_main.pdf")
  overlay_pdf_name <- overlay_pdf_name %||% paste0("figure_", plot_type, "_overlay.pdf")
  combined_pdf_name <- combined_pdf_name %||% paste0("figure_", plot_type, "_combined.pdf")
  
  # If diagnostic mode, modify overlay filename
  if (create_diagnostic) {
    overlay_pdf_name <- sub("\\.pdf$", "_diagnostic.pdf", overlay_pdf_name)
  }
  
  # 1. Save main figure with color legend
  pdf(main_pdf_name, height = main_height, width = main_width)
  main_plot <- plot_grid(plot_obj, legend_obj, ncol = 2, rel_widths = rel_widths, align = "h")
  print(main_plot)
  dev.off()
  
  # 2. Create and save overlay with duplicate structure
  overlay_plot <- f.create_duplicate_structure_overlay(
    plot_obj = plot_obj,
    legend_obj = legend_obj,
    rel_widths = rel_widths,
    legend_xmin = legend_xmin,
    legend_xmax = legend_xmax,
    legend_ymin = legend_ymin,
    legend_ymax = legend_ymax,
    preserve_axis_text = preserve_axis_text,  # Pass axis text preservation parameter
    create_diagnostic = create_diagnostic
  )
  
  pdf(overlay_pdf_name, height = main_height, width = main_width)
  par(bg = "transparent")  # Set transparent background
  print(overlay_plot)
  dev.off()
  
  message(paste0(plot_type, " PDFs created successfully."))
  
  # Return file paths
  result <- list(
    main = main_pdf_name,
    overlay = overlay_pdf_name,
    combined = combined_pdf_name
  )
  
  # Add the diagnostic file path if created
  if (create_diagnostic) {
    result$diagnostic <- overlay_pdf_name
  }
  
  return(result)
}

# Function to combine PDFs with error handling and multiple methods
f.combine_duplicate_pdfs <- function(
  files,
  pdftk_options = NULL,
  gs_options = NULL
) {
  # Helper function for null values
  "%||%" <- function(x, y) {
    if (is.null(x)) y else x
  }
  
  # Default options for pdftk and gs if not provided
  pdftk_options <- pdftk_options %||% ""  # No extra options by default
  gs_options <- gs_options %||% ""  # No extra options by default
  
  # Check if pdftk is available
  has_pdftk <- system("which pdftk", ignore.stdout = TRUE, ignore.stderr = TRUE) == 0
  
  # Check if ghostscript is available
  has_gs <- system("which gs", ignore.stdout = TRUE, ignore.stderr = TRUE) == 0
  
  success <- FALSE
  
  # Combine PDFs using available tool
  if (has_pdftk) {
    # Try stamp mode with optional parameters
    cmd <- sprintf("pdftk %s stamp %s %s output %s", 
                   files$main, files$overlay, pdftk_options, files$combined)
    result <- system(cmd)
    
    if (result == 0) {
      message("PDFs combined using pdftk stamp mode")
      success <- TRUE
    } else {
      # Try alternative modes if stamp fails
      alt_modes <- list(
        list(name = "background", cmd = sprintf("pdftk %s background %s %s output %s", 
                                               files$main, files$overlay, pdftk_options, files$combined)),
        list(name = "multistamp", cmd = sprintf("pdftk %s multistamp %s %s output %s", 
                                               files$main, files$overlay, pdftk_options, files$combined))
      )
      
      for (mode in alt_modes) {
        result <- system(mode$cmd)
        if (result == 0) {
          message(paste0("PDFs combined using pdftk ", mode$name, " mode"))
          success <- TRUE
          break
        }
      }
      
      if (!success) {
        message("All pdftk modes failed")
      }
    }
  } else if (has_gs) {
    # Use ghostscript as fallback with optional parameters
    cmd <- sprintf("gs -q -dNOPAUSE -dBATCH -sDEVICE=pdfwrite %s -sOutputFile=%s %s %s", 
                   gs_options, files$combined, files$main, files$overlay)
    result <- system(cmd)
    
    if (result == 0) {
      message("PDFs combined using Ghostscript")
      success <- TRUE
    } else {
      message("Ghostscript command failed")
    }
  } else {
    message("Neither pdftk nor Ghostscript found. Please install one of these tools.")
  }
  
  # Verify the combined file exists
  if (success && file.exists(files$combined)) {
    message("Combined PDF created successfully: ", files$combined)
    return(TRUE)
  } else {
    message("Error: Combined PDF was not created successfully.")
    return(FALSE)
  }
}

# Function to optimize/compress PDF after combining with high-quality settings
f.optimize_pdf <- function(
  input_pdf,
  output_pdf = NULL,
  quality = "prepress",   # Options: screen, ebook, printer, prepress
  compatibility = "1.5",  # PDF compatibility level
  embed_fonts = TRUE,
  compress_images = TRUE
) {
  # Helper function for null values
  "%||%" <- function(x, y) {
    if (is.null(x)) y else x
  }
  
  # Use input filename with _optimized suffix if no output name provided
  if (is.null(output_pdf)) {
    output_pdf <- sub("\\.pdf$", "_optimized.pdf", input_pdf)
  }
  
  # Check if ghostscript is available
  has_gs <- system("which gs", ignore.stdout = TRUE, ignore.stderr = TRUE) == 0
  
  if (!has_gs) {
    message("Ghostscript not found. Cannot optimize PDF.")
    return(FALSE)
  }
  
  # Build options for Ghostscript
  gs_options <- c(
    sprintf("-dPDFSETTINGS=/%s", quality),
    sprintf("-dCompatibilityLevel=%s", compatibility),
    "-dPrinted=false"  # Optimize for screen viewing
  )
  
  # Add font embedding if requested
  if (embed_fonts) {
    gs_options <- c(gs_options,
                    "-dEmbedAllFonts=true",
                    "-dSubsetFonts=true",
                    "-dMaxSubsetPct=100")
  }
  
  # Add image compression if requested
  if (compress_images) {
    gs_options <- c(gs_options,
                    "-dColorImageDownsampleType=/Bicubic",
                    "-dGrayImageDownsampleType=/Bicubic",
                    "-dMonoImageDownsampleType=/Bicubic")
  }
  
  # Combine options into a single string
  gs_options_str <- paste(gs_options, collapse = " ")
  
  # Ghostscript command for optimization
  cmd <- sprintf("gs -sDEVICE=pdfwrite -dNOPAUSE -dQUIET -dBATCH %s -sOutputFile=%s %s",
                gs_options_str, output_pdf, input_pdf)
  
  result <- system(cmd)
  
  if (result == 0) {
    message("PDF optimized successfully: ", output_pdf)
    
    # Get file sizes for reporting
    original_size <- file.size(input_pdf) / (1024 * 1024)  # Convert to MB
    optimized_size <- file.size(output_pdf) / (1024 * 1024)
    reduction <- (1 - optimized_size/original_size) * 100
    
    message(sprintf("File size reduced from %.2f MB to %.2f MB (%.1f%% reduction)",
                   original_size, optimized_size, reduction))
    
    return(TRUE)
  } else {
    message("PDF optimization failed")
    return(FALSE)
  }
}

# Main function to run the duplicate structure test
# With fully parameterized options
f.run_duplicate_structure_test <- function(
  # Required parameters
  plot_obj,
  legend_obj,
  
  # Identification parameters
  plot_type = "two",
  
  # File parameters
  main_pdf_name = NULL,
  overlay_pdf_name = NULL,
  combined_pdf_name = NULL,
  optimized_pdf_name = NULL,
  
  # Dimension parameters
  main_width = 8.5,
  main_height = 11,
  rel_widths = c(14, 1),
  
  # Legend positioning parameters
  legend_xmin = NULL,
  legend_xmax = 1,
  legend_ymin = 0,
  legend_ymax = 0.25,
  
  # Display parameters
  preserve_axis_text = TRUE,  # Added parameter for axis text preservation
  
  # PDF combination parameters
  pdftk_options = NULL,
  gs_options = NULL,
  
  # Optimization parameters
  optimize_pdf = TRUE,
  quality = "prepress",    # Options: screen, ebook, printer, prepress
  compatibility = "1.5",   # PDF compatibility level
  embed_fonts = TRUE,
  compress_images = TRUE,
  
  # Diagnostic parameters
  create_diagnostic = FALSE,
  
  # Cleanup parameters
  delete_intermediate = FALSE
) {
  # Helper function for null values
  "%||%" <- function(x, y) {
    if (is.null(x)) y else x
  }
  
  # Set default filenames based on plot_type
  combined_pdf_name <- combined_pdf_name %||% paste0("figure_", plot_type, "_combined.pdf")
  optimized_pdf_name <- optimized_pdf_name %||% paste0("figure_", plot_type, "_optimized.pdf")
  
  # Create PDFs with duplicate structure
  files <- f.save_duplicate_structure_pdfs(
    plot_obj = plot_obj,
    legend_obj = legend_obj,
    plot_type = plot_type,
    main_pdf_name = main_pdf_name,
    overlay_pdf_name = overlay_pdf_name,
    combined_pdf_name = combined_pdf_name,
    main_width = main_width,
    main_height = main_height,
    rel_widths = rel_widths,
    legend_xmin = legend_xmin,
    legend_xmax = legend_xmax,
    legend_ymin = legend_ymin,
    legend_ymax = legend_ymax,
    preserve_axis_text = preserve_axis_text,  # Pass axis text preservation parameter
    create_diagnostic = create_diagnostic
  )
  
  # Skip PDF combination if only creating diagnostic
  if (create_diagnostic) {
    message("Diagnostic overlay created. Skipping PDF combination.")
    message("To see coordinate grid, check: ", files$diagnostic)
    return(TRUE)
  }
  
  # Combine PDFs
  success <- f.combine_duplicate_pdfs(
    files = files,
    pdftk_options = pdftk_options,
    gs_options = gs_options
  )
  
  # Optimize the combined PDF if requested
  if (success && optimize_pdf) {
    f.optimize_pdf(
      input_pdf = files$combined, 
      output_pdf = optimized_pdf_name,
      quality = quality,
      compatibility = compatibility,
      embed_fonts = embed_fonts,
      compress_images = compress_images
    )
    # Update the combined PDF reference to the optimized version
    files$final <- optimized_pdf_name
  } else {
    files$final <- files$combined
  }
  
  # Delete intermediate files if requested
  if (success && delete_intermediate) {
    file.remove(files$main)
    file.remove(files$overlay)
    if (optimize_pdf) {
      file.remove(files$combined)  # Remove the unoptimized combined file
    }
    message("Intermediate files deleted.")
  }
  
  if (success) {
    message(paste0(plot_type, " figure completed successfully! Check: ", files$final))
  } else {
    message(paste0(plot_type, " figure encountered issues."))
  }
  
  return(success)
}
```

# new functions

## vertical legend function
```{r}
# Function to create a horizontal or vertical eye legend - Version 7
# Dynamically adjusts dimensions based on orientation
f.eye_legend_horiz_to_vert_v7 <- function(
  # Basic dimensions with dynamic orientation handling
  long_side_dimension = 800,   # Longer side of the plot
  short_side_dimension = 100,  # Shorter side of the plot
  is_vertical = FALSE,         # Control orientation
  
  # Spacing parameters
  left_margin = 40,         # Space at left edge
  right_margin = 40,        # Space at right edge
  icon_text_gap = 20,       # Space between icon and its text
  element_gap = 60,         # Space between text and next icon
  
  # Flexible spacing ratios
  margin_ratio = NULL,      # Optional ratio-based margin calculation
  inter_element_ratio = NULL, # Optional ratio-based element spacing
  
  # Sizing parameters
  text_size = 10,           # Base text size
  circle_size = 20,         # Radius of the station circle
  aletta_scale = 2.5,       # Scale factor for Aletta symbol
  bud_scale = 0.18,         # Scale factor for Bud hurricane image
  icon_scale_factor = 1,    # Global scaling for all icons
  
  # Circle styling parameters
  circle_parameters = NULL, # Circle styling parameters
  orange_circle_dash_length = 1  # Parameter to control dash spacing
) {
  # Helper function for null values
  "%||%" <- function(x, y) {
    if (is.null(x)) y else x
  }
  
  # Dynamically set plot dimensions based on orientation
  if (is_vertical) {
    plot_width <- short_side_dimension
    plot_height <- long_side_dimension
  } else {
    plot_width <- long_side_dimension
    plot_height <- short_side_dimension
  }
  
  # Calculate margins using ratio if provided
  if (!is.null(margin_ratio)) {
    total_margin_width <- plot_width * margin_ratio
    left_margin <- total_margin_width / 2
    right_margin <- total_margin_width / 2
  }
  
  # Calculate element gap using ratio if provided
  if (!is.null(inter_element_ratio)) {
    element_gap <- plot_width * inter_element_ratio
  }
  
  # Adjust scaling for icons
  adjusted_circle_size <- circle_size * icon_scale_factor
  adjusted_aletta_scale <- aletta_scale * icon_scale_factor
  adjusted_bud_scale <- bud_scale * icon_scale_factor
  
  # Calculate usable width (accounting for margins)
  usable_width <- plot_width - left_margin - right_margin
  
  # Determine orientation-specific parameters
  if (!is_vertical) {
    # Horizontal layout
    x_bud <- left_margin
    x_bud_text <- x_bud + icon_text_gap
    x_aletta <- x_bud_text + element_gap
    x_aletta_text <- x_aletta + icon_text_gap
    x_station <- x_aletta_text + element_gap
    x_station_text <- x_station + icon_text_gap
    y_center <- plot_height / 2
  } else {
    # Vertical layout
    y_bud <- plot_height - left_margin
    y_bud_text <- y_bud - icon_text_gap
    y_aletta <- y_bud_text - element_gap
    y_aletta_text <- y_aletta - icon_text_gap
    y_station <- y_aletta_text - element_gap
    y_station_text <- y_station - icon_text_gap
    x_center <- plot_width / 2
  }
  
  # Extract styling from circle_parameters
  if (!is.null(circle_parameters)) {
    circle_color1 <- circle_parameters["circle_color1"] %||% "white"
    circle_color2 <- circle_parameters["circle_color2"] %||% "#E65832"
    base <- as.numeric(circle_parameters["base"] %||% "5.0")
    outline <- as.numeric(circle_parameters["outline"] %||% "7.5")
  } else {
    # Default values if circle_parameters is NULL
    circle_color1 <- "white"
    circle_color2 <- "#E65832"
    base <- 5.0
    outline <- 7.5
  }
  
  # Set line thicknesses for legend
  legend_outline <- outline * 0.5
  legend_base <- base * 0.5
  
  # Text labels
  text1 <- "TC Bud Eye"
  text2 <- "TC Aletta Eye"
  text3 <- "200km Diameter\nStation 3.5"
  
  # Create base plot
  p <- ggplot() +
    # Clean theme with minimal margins
    theme_void() +
    theme(
      plot.margin = margin(0, 0, 0, 0),
      panel.border = element_blank(),
      panel.spacing = unit(0, "mm")
    ) +
    coord_cartesian(xlim = c(0, plot_width), ylim = c(0, plot_height), expand = FALSE)
  
  # Add elements based on orientation
  if (!is_vertical) {
    # Horizontal layout
    p <- p +
      # Station circle data using simple coordinates
      geom_path(data = data.frame(
        x = x_station + adjusted_circle_size * cos(seq(0, 2*pi, length.out = 100)),
        y = y_center + adjusted_circle_size * sin(seq(0, 2*pi, length.out = 100))
      ), aes(x, y), color = circle_color1, linewidth = legend_outline, 
        linetype = "solid", alpha = 1, inherit.aes = FALSE) +
      
      # Orange dashed circle
      geom_path(data = data.frame(
        x = x_station + adjusted_circle_size * cos(seq(0, 2*pi, length.out = 100)),
        y = y_center + adjusted_circle_size * sin(seq(0, 2*pi, length.out = 100))
      ), aes(x, y), color = circle_color2, linewidth = legend_base, 
        linetype = orange_circle_dash_length, alpha = 1, inherit.aes = FALSE) +
      
      # Aletta eye
      geom_point(data = data.frame(x = x_aletta, y = y_center), 
                 aes(x, y), shape = aletta_symbol, color = aletta_color, 
                 fill = aletta_color, size = aletta_size * adjusted_aletta_scale) +
      
      # Bud eye
      geom_image(data = data.frame(x = x_bud, y = y_center, 
                                   image = b$image[1]), 
                 aes(x, y, image = image), size = adjusted_bud_scale) +
      
      # Text labels
      annotate("text", x = x_bud_text, y = y_center, label = text1, 
               hjust = 0, size = text_size/2.5) +
      annotate("text", x = x_aletta_text, y = y_center, label = text2, 
               hjust = 0, size = text_size/2.5) +
      annotate("text", x = x_station_text, y = y_center, label = text3, 
               hjust = 0, size = text_size/2.5)
  } else {
    # Vertical layout
    p <- p +
      # Station circle data using simple coordinates
      geom_path(data = data.frame(
        x = x_center + adjusted_circle_size * cos(seq(0, 2*pi, length.out = 100)),
        y = y_station + adjusted_circle_size * sin(seq(0, 2*pi, length.out = 100))
      ), aes(x, y), color = circle_color1, linewidth = legend_outline, 
        linetype = "solid", alpha = 1, inherit.aes = FALSE) +
      
      # Orange dashed circle
      geom_path(data = data.frame(
        x = x_center + adjusted_circle_size * cos(seq(0, 2*pi, length.out = 100)),
        y = y_station + adjusted_circle_size * sin(seq(0, 2*pi, length.out = 100))
      ), aes(x, y), color = circle_color2, linewidth = legend_base, 
        linetype = orange_circle_dash_length, alpha = 1, inherit.aes = FALSE) +
      
      # Aletta eye
      geom_point(data = data.frame(x = x_center, y = y_aletta), 
                 aes(x, y), shape = aletta_symbol, color = aletta_color, 
                 fill = aletta_color, size = aletta_size * adjusted_aletta_scale) +
      
      # Bud eye
      geom_image(data = data.frame(x = x_center, y = y_bud, 
                                   image = b$image[1]), 
                 aes(x, y, image = image), size = adjusted_bud_scale) +
      
      # Text labels
      annotate("text", x = x_center, y = y_bud_text, label = text1, 
               hjust = 1, angle = 90, size = text_size/2.5) +
      annotate("text", x = x_center, y = y_aletta_text, label = text2, 
               hjust = 1, angle = 90, size = text_size/2.5) +
      annotate("text", x = x_center, y = y_station_text, label = text3, 
               hjust = 1, angle = 90, size = text_size/2.5)
  }
  
  return(p)
}
```
## main figure function

```{r}
f.create_dual_legend_main_figure <- function(
  # Required parameters
  plot_obj,
  legend_obj,
  
  # Identification parameters
  plot_type = "two",
  
  # File parameters
  main_pdf_name = NULL,
  overlay_pdf_name = NULL,
  combined_pdf_name = NULL,
  optimized_pdf_name = NULL,
  
  # Dimension parameters
  main_width = 8.5,
  main_height = 11,
  rel_widths = c(14, 1),
  
  # Legend positioning parameters
  legend_xmin = NULL,
  legend_xmax = 1,
  legend_ymin = 0,
  legend_ymax = 0.25,
  
  # New additional parameters for dual legends
  color_legend_obj = NULL,
  eye_legend_obj = NULL,
  color_legend_xmin = NULL,
  color_legend_xmax = 1,
  color_legend_ymin = 0,
  color_legend_ymax = 0.25,
  eye_legend_xmin = NULL,
  eye_legend_xmax = 1,
  eye_legend_ymin = 0,
  eye_legend_ymax = 0.15,
  
  # PDF combination parameters
  pdftk_options = NULL,
  gs_options = NULL,
  
  # Optimization parameters
  optimize_pdf = TRUE,
  quality = "prepress",
  compatibility = "1.5",
  embed_fonts = TRUE,
  compress_images = TRUE,
  
  # Other parameters
  preserve_axis_text = TRUE,
  create_diagnostic = FALSE,
  delete_intermediate = FALSE
) {
  # Helper function for null values
  "%||%" <- function(x, y) {
    if (is.null(x)) y else x
  }
  
  # Set default filenames based on plot_type
  main_pdf_name <- main_pdf_name %||% paste0("figure_", plot_type, "_main.pdf")
  overlay_pdf_name <- overlay_pdf_name %||% paste0("figure_", plot_type, "_overlay.pdf")
  combined_pdf_name <- combined_pdf_name %||% paste0("figure_", plot_type, "_combined.pdf")
  optimized_pdf_name <- optimized_pdf_name %||% paste0("figure_", plot_type, "_optimized.pdf")
  
  # 1. Save main figure with color legend
  pdf(main_pdf_name, height = main_height, width = main_width)
  main_plot <- plot_grid(plot_obj, color_legend_obj %||% legend_obj, ncol = 2, rel_widths = rel_widths, align = "h")
  print(main_plot)
  dev.off()
  
  # 2. Create overlay plot with transparent background
  overlay_plot <- plot_obj + 
    theme(
      panel.background = element_rect(fill = NA, color = NA),
      plot.background = element_rect(fill = NA, color = NA),
      panel.grid = element_blank(),
      axis.text = if (preserve_axis_text) element_text() else element_text(color = NA),
      axis.title = element_text(color = NA),
      axis.ticks = if (preserve_axis_text) element_line() else element_line(color = NA),
      legend.position = "none",
      plot.margin = margin(0, 0, 0, 0)
    )
  
  # 3. Create overlay structure
  overlay_structure <- plot_grid(
    overlay_plot, 
    ggplot() + theme_void(),  # Empty top legend space
    ncol = 2, 
    rel_widths = rel_widths, 
    align = "h"
  )
  
  # 4. Add legends to overlay
  final_overlay <- overlay_structure + 
    annotation_custom(
      grob = if(is.ggplot(eye_legend_obj)) ggplotGrob(eye_legend_obj) else eye_legend_obj,
      xmin = eye_legend_xmin %||% (1 - (rel_widths[2] / sum(rel_widths))),
      xmax = eye_legend_xmax,
      ymin = eye_legend_ymin,
      ymax = eye_legend_ymax
    )
  
  # 5. Save overlay PDF
  pdf(overlay_pdf_name, height = main_height, width = main_width)
  print(final_overlay)
  dev.off()
  
  # 6. Combine PDFs
  files <- list(
    main = main_pdf_name,
    overlay = overlay_pdf_name,
    combined = combined_pdf_name
  )
  
  success <- f.combine_duplicate_pdfs(
    files = files,
    pdftk_options = pdftk_options,
    gs_options = gs_options
  )
  
  # 7. Optimize PDF if requested
  if (success && optimize_pdf) {
    f.optimize_pdf(
      input_pdf = files$combined, 
      output_pdf = optimized_pdf_name,
      quality = quality,
      compatibility = compatibility,
      embed_fonts = embed_fonts,
      compress_images = compress_images
    )
    files$final <- optimized_pdf_name
  } else {
    files$final <- files$combined
  }
  
  # 8. Delete intermediate files if requested
  if (success && delete_intermediate) {
    file.remove(files$main)
    file.remove(files$overlay)
    if (optimize_pdf) {
      file.remove(files$combined)
    }
    message("Intermediate files deleted.")
  }
  
  # Return files for reference
  return(files)
}
```




vertical legend
```{r}
# Create the vertical eye legend
legend_vertical <- f.eye_legend_horiz_to_vert_v7(
  long_side_dimension = 800,
  short_side_dimension = 100,
  is_vertical = TRUE,
  left_margin = 80,       # Increased margin
  right_margin = 80,      # Increased margin
  icon_text_gap = 30,     # Increased icon-text gap
  element_gap = 100,      # Increased element spacing
  margin_ratio = 0.15,    # Adjusted margin ratio
  inter_element_ratio = 0.17, # Adjusted inter-element ratio
  text_size = 10,
  circle_size = 22,
  aletta_scale = 3.0,
  bud_scale = 0.22,
  icon_scale_factor = 1.2,
  orange_circle_dash_length = 1  # Default dash length
)
```



# final plotiing
```{r}

# Generate the dual legend figure
# Set the working directory to the figures folder
setwd(wd)
setwd(fig)



# Generate the dual legend figure
f.create_dual_legend_main_figure(
  plot_obj = p,
  color_legend_obj = legend,  # Color bar legend from original code
  eye_legend_obj = legend_vertical,
  
  # Plot type identifier (optional)
  plot_type = "two",
  
  # Optional custom PDF filenames (if not provided, defaults will be used)
  main_pdf_name = "figure_two_main.pdf",
  overlay_pdf_name = "figure_two_eye_overlay.pdf",
  combined_pdf_name = "figure_two_both_legends.pdf",
  optimized_pdf_name = "figure_two_both_legends_optimized.pdf",
  
  # Dimensions and layout
  main_width = 8.5,
  main_height = 11,
  rel_widths = c(14, 1),
  
  # Positioning for color legend
  color_legend_xmin = 0.75,   # Right side of the figure 
  color_legend_xmax = 0.99,   # Not quite to the edge
  color_legend_ymin = 0,      # Bottom of the figure
  color_legend_ymax = 0.25,   # About 1/4 of the way up
  
  # Positioning for eye legend
  eye_legend_xmin = 0.75,     # Right side of the figure 
  eye_legend_xmax = 0.99,     # Not quite to the edge
  eye_legend_ymin = -0.1,     # Position slightly below the plot
  eye_legend_ymax = 0.15,     # About 1/4 of the way up
  
  # New optional PDF combination parameters
  pdftk_options = NULL,       # Additional options for pdftk PDF tool
  gs_options = NULL,          # Additional options for Ghostscript
  
  # PDF optimization parameters
  optimize_pdf = TRUE,        # Whether to optimize the final PDF
  quality = "prepress",       # Optimization quality level
  compatibility = "1.5",      # PDF compatibility version
  embed_fonts = TRUE,         # Embed fonts in the PDF
  compress_images = TRUE,     # Compress images in the PDF
  
  # Other options
  preserve_axis_text = TRUE,  # Keep axis text visible in overlay
  create_diagnostic = FALSE,  # Create diagnostic overlay (if supported)
  delete_intermediate = FALSE # Delete intermediate PDF files
)
```


