---
title: "poc_flux_and_TC_and_CHl_and_SST"
author: "Brandon M. Genco"
date: "06/15/2023"
output: html_document
---
code re purposed from "Hurricane 0instu_matchup_2.rmd"
and then "poc_flux_and_TC_and_CHl_and_SST.rmd"

# Setup
## Directories and defaults
Use r proj file for relative directories
see: https://yihui.org/knitr/options/


```{r setup}
rm(list=ls())
# relative directories
robj<-"r_objects"
fig<-"../../figures"
gis_data<-"../../data/gis_data"
output<-"../../output"

sst_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_sst_netcdf"
chl_data<-"../../data/POC_Flux_data_sets/annual_vgpm_modis_chl_netcdf"
 
#absolute directory
# drop_img<-"/home/brandon/Dropbox/MERCED/dissertation/presentations/images"

knitr::opts_chunk$set(echo =FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

## packages and working directory

Installed custom hurdat package using r markdown menu
* download  tar from archive as no longer maintained on cran repository
* https://cran.r-project.org/src/contrib/Archive/HURDAT/
+ include as git submodule instead

```{r}
wd<-getwd()

f.ipak <- function(pkg){
  # loads packages, quietly, given by a vector of package names e.g., pkg<-c("ggplot", "tidyverse")
  # will install  packages listed , and their dependencies, if needed.
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg))
    install.packages(new.pkg, dependencies = TRUE, quiet=T, verbose = F)
  sapply(pkg, require, character.only = TRUE, quietly = FALSE, warn.conflicts=F)
}

# packages<-c("stars", "gridExtra", "cowplot", "sf", "ggspatial","stringr","sp", "rgdal",  "rgeos", "raster","readr" ,"tidyverse", "ggplot2", "lubridate",  "ggthemes", "data.table", "reshape2", "RColorBrewer", "marmap", "extrafont", "oce", "MODIS", "measurements")  # set packages here
# tidyverse: is all of the following packages: ggplot2, dplyr, tidyr, readr, purr, tibble, sringr, & forcats.

packages<-c("sp", "rgdal",  "rgeos", "raster", "readr", "tidyverse", "lubridate",  "ggthemes",  "sf", "cmocean", "ncdf4", "RNetCDF",  "plot3D", "tidync", "devtools", "stars", "ncmeta", "maps", "oce", "data.table", "fasterize", "RStoolbox", "scales", "purrr", "HURDAT", "ggpattern")

# "HURDAT",

f.ipak(packages)
# lapply(packages, require, character.only = TRUE)
# rm(f.ipak, packages)
print(paste0("Current Working Directory is ", getwd()))

```

## functions

```{r}
f.grid_square_area2<-function(x) {
  x.area<-vector(mode="numeric", length = nrow(x)) 
  
  for(i in 1:length(x.area)){
    bbox<-st_bbox(x[[2]][[i]])
    box<-vector(mode="numeric", length=4)
    names(box)<-c("xmin","ymin","ymax", "xmax")
    box$ymin<-round(bbox$ymin[[1]]-(5/120),3)
    box$ymax<-round(bbox$ymax[[1]]+(5/120),3)
    box$xmin<-round(bbox$xmin[[1]] +-(5/120),3)
    box$xmax<-round(bbox$xmax[[1]] +(5/120),3)
    x.area[i]<- rgeos::bbox2SP(n = box$ymax[[1]], s = box$ymin[[1]], w = box$xmin[[1]], e = box$xmax[[1]],
                               proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")) %>% st_as_sf(.,) %>% st_area(.,) %>% round(., -1)
  }
  sum_grid_area<-sum(x.area)
  x$value<-x.area
  y<-vector(mode = "list", length=2)
  names(y)<-c("grid_area", "sum_grid_area")
  y$grid_area<-x
  y$sum_grid_area<-sum_grid_area
  
  return(y)}

f.sst_data_nc<-function(z){
  
  sst_integrated<-as.data.frame(matrix(ncol = 7, nrow =length(files)))
  names(sst_integrated)<-c("date",  "SST_mean (area weighted)", "SST_mean (basic)", "SST_median", "SST_variance", "window_area (m^2)", "sum_grid_area (m^2)")
  
  for(i in 1:length(files)){
    file<-files[i]
    t<-tidync(file)%>% hyper_filter(lat = lat >= min(z$lat) & lat <= max(z$lat), lon = lon>= min(z$lon) & lon<= max(z$lon)) %>% hyper_tibble()
    # t$sst[t$sst == -9999] <- NA
    x<-t$sst
    x.sf<-t%>%st_as_sf(., coords = c("lon", "lat" ), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
    
    bbox<-st_bbox(x.sf)
    box<-vector(mode="numeric", length=4)
    names(box)<-c("xmin","ymin","ymax", "xmax")
    box$ymin<-round(bbox$ymin[[1]]-(5/120),3)
    box$ymax<-round(bbox$ymax[[1]]+(5/120),3)
    box$xmin<-round(bbox$xmin[[1]] +-(5/120),3)
    box$xmax<-round(bbox$xmax[[1]] +(5/120),3)
    
    area <- rgeos::bbox2SP(n = box$ymax[[1]], s = box$ymin[[1]], w = box$xmin[[1]], e = box$xmax[[1]],
                           proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")) %>% st_as_sf(.,) %>% st_area(.,)
    rm(box, bbox)
    
    t<-str_split(file, '\\.')
    t<-t[[1]][2]
    t<-str_split(t, "")
    y<-c(t[[1]][1:4])%>% toString(.) %>% gsub(",","",.) %>% gsub(" ","",.)   
    yd<-c(t[[1]][5:7])%>% toString(.) %>% gsub(",","",.) %>% gsub(" ","",.)
    origin<-toString(c(y,"-01-01")) %>% gsub(",","",.) %>% gsub(" ","",.)
    
    
    names(x.sf)<-c("value", "geometry")
    y<-f.grid_square_area2(x.sf)
    q<-y$grid_area$value/y$sum_grid_area
    wa<-sum(q*x)
   
    sst_integrated[i,1]<-as.character(as.Date(as.numeric(yd), origin=origin)) # date  
    sst_integrated[i,2]<-wa
    sst_integrated[i,3]<-mean(x) # vgpm_median
    sst_integrated[i,4]<-median(x) # vgpm_mean
    sst_integrated[i,5]<-var(x) # vgpm_variance
    sst_integrated[i,6]<-as.numeric(area) # window_area (m^2) 
    sst_integrated[i,7]<-y$sum_grid_area # sum_grid_area (m^2)
    
  }
  
  
  # n<-names(vgpm_integrated)
  # vgpm_integrated<-dplyr::select(vgpm_integrated, n[1], n[12], n[13], n[6], n[7], n[9], n[10], n[8],n[2], n[3],  n[11], n[4], n[5] )
  
  return(sst_integrated)}

f.chl_data_nc<-function(z){
  
  chl_integrated<-as.data.frame(matrix(ncol = 7, nrow =length(files)))
  names(chl_integrated)<-c("date",  "chl_mean (area weighted)", "chl_mean (basic)", "chl_median", "chl_variance", "window_area (m^2)", "sum_grid_area (m^2)")
  
  for(i in 1:length(files)){
    file<-files[i]
    t<-tidync(file)%>% hyper_filter(lat = lat >= min(z$lat) & lat <= max(z$lat), lon = lon>= min(z$lon) & lon<= max(z$lon)) %>% hyper_tibble()
    # t$sst[t$sst == -9999] <- NA
    x<-t$chl
    x.sf<-t%>%st_as_sf(., coords = c("lon", "lat" ), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
    
    bbox<-st_bbox(x.sf)
    box<-vector(mode="numeric", length=4)
    names(box)<-c("xmin","ymin","ymax", "xmax")
    box$ymin<-round(bbox$ymin[[1]]-(5/120),3)
    box$ymax<-round(bbox$ymax[[1]]+(5/120),3)
    box$xmin<-round(bbox$xmin[[1]] +-(5/120),3)
    box$xmax<-round(bbox$xmax[[1]] +(5/120),3)
    
    area <- rgeos::bbox2SP(n = box$ymax[[1]], s = box$ymin[[1]], w = box$xmin[[1]], e = box$xmax[[1]],
                           proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")) %>% st_as_sf(.,) %>% st_area(.,)
    rm(box, bbox)
    
    t<-str_split(file, '\\.')
    t<-t[[1]][2]
    t<-str_split(t, "")
    y<-c(t[[1]][1:4])%>% toString(.) %>% gsub(",","",.) %>% gsub(" ","",.)   
    yd<-c(t[[1]][5:7])%>% toString(.) %>% gsub(",","",.) %>% gsub(" ","",.)
    origin<-toString(c(y,"-01-01")) %>% gsub(",","",.) %>% gsub(" ","",.)
    
    
    names(x.sf)<-c("value", "geometry")
    y<-f.grid_square_area2(x.sf)
    q<-y$grid_area$value/y$sum_grid_area
    wa<-sum(q*x)
    
    chl_integrated[i,1]<-as.character(as.Date(as.numeric(yd), origin=origin)) # date  
    chl_integrated[i,2]<-wa
    chl_integrated[i,3]<-mean(x) # vgpm_median
    chl_integrated[i,4]<-median(x) # vgpm_mean
    chl_integrated[i,5]<-var(x) # vgpm_variance
    chl_integrated[i,6]<-as.numeric(area) # window_area (m^2) 
    chl_integrated[i,7]<-y$sum_grid_area # sum_grid_area (m^2)
    
  }
  
  
  # n<-names(vgpm_integrated)
  # vgpm_integrated<-dplyr::select(vgpm_integrated, n[1], n[12], n[13], n[6], n[7], n[9], n[10], n[8],n[2], n[3],  n[11], n[4], n[5] )
  
  return(chl_integrated)}
```


# Important objects and data sets
## temp load/save works save for next steps

## load basic hurdat

```{r}
setwd(wd)
setwd(robj)
# h<-get_hurdat(basin="EP")
# saveRDS(h, "hurdat.R")

h<-readRDS("hurdat.R")
h$DateTime<-with_tz(h$DateTime, tz="UTC")
```



## stations and buffer

```{r}
setwd(wd)
setwd(robj)

radii<-100000 ## radius in km for POC select

# radii<-2*radii ## for selecting TC that intesect

stations_positions_list<-readRDS("OC1806A_stations_positions_list.R")


st<-stations_positions_list[[3]][4,cbind(2,3)]
st<-sf::st_as_sf(st, coords =c("longitude", "latitude"),  crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
flat<-sf::st_transform(st, "+proj=aeqd +lat_0=18.5005 +lon_0=-108.502" )
circle_3.5<-sf::st_buffer(flat, dist=radii)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

rm(st, flat, stations_positions_list)

```


# loading POC
* Important set end date to remove NA's in in EF and SST
** 2022-08-13 & 2020-09-05m 
*** TC overpass in thes dates?
**missing SST 2021-0907


```{r}
setwd(wd)
setwd(robj)
# 
# end_date<-'2020-08-12'


# data<-read_rds("vgpm_integrated_20220512.R")
data<-read_rds("vgpm_integrated_all_years_202200607.R")
poc<-data$st3.5
end_date<-max(poc$date)

sst<-readRDS("st35_sst_modis.R")
chl<-readRDS("st35_chl_modis.R")

poc$date<-ymd(poc$date)
poc<-poc%>%filter(date <= end_date)

x<-poc
window_area<-round((x$`window_area (m^2)`[1]*1e-6),0)

# lab_avg<-'8-Day resolution: Non-lagged EF (proportion of modeled VGPM). Colored lines are individual tropical disturbances that pass within the export flux box around station 3.5: Orange = Hurricane strength,  Blue = less than " " '
lab_total<-paste0("Station ", "3.5", ":", " Total Export Flux - ", window_area, " km^2 area")


x<-select(x, date, `mean_export_flux (mgC/m^2/day) for_window_area (total/sum_grid_area)`, `total_export_flux (mgC/day)`)

names(x)<-c("date", "avg", "ef")
x$ef<-x$ef/1000000


y<-select(chl, date, 'chl_mean (area weighted)')
names(y)<-c("date", "chl")
y$date<-ymd(y$date)

z<-select(sst, date, `SST_mean (area weighted)`)
names(z)<-c("date", "sst")
z$date<-ymd(z$date)


y<-y%>%filter(date <= end_date)
z<-z%>%filter(date <= end_date)

rm(data, sst, chl)

```


# selecting TCs by space and time
-requires POC for time window
_
```{r}

bbox<-st_bbox(circle_3.5)

# x<-filter(h, Status == "HU") %>% filter(., DateTime >=date(min(poc$date))-60) # save 'h' in order to adjust function variables if needed.
g<-filter(h, DateTime >=date(min(poc$date))-60) # save 'h' in order to adjust function variables if needed.
h.pts<- sf::st_as_sf(g, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
sf::st_crop(., c(xmin=bbox$xmin[[1]], ymin=bbox$ymin[[1]], xmax=bbox$xmax[[1]], ymax=bbox$ymax[[1]])) #subset by user defined 

# h.pts<-st_difference(h.pts, st_combine(st_geometry(cl))) # remove all points over land
rm(g)

```


## split and recombine
```{r}
t<-h.pts 
st_geometry(t)<-NULL
t$ymin<--Inf
t$ymax<-Inf
# t$DateTime<-as.Date(t$DateTime)
t$DateTime<-as_datetime(t$DateTime)

 unique(t$Status)
 
# see:  https://www.nhc.noaa.gov/data/hurdat/hurdat2-format-atl-1851-2021.pdf
#"TS" tropical cyclone of tropical storm intensity (34-63 knots)
# "TD" Tropical cyclone of tropical depression intensity (< 34 knots)
# LO – A low that is neither a tropical cyclone, a subtropical cyclone, nor an extratropical cyclone (of any intensity)
# DB – Disturbance (of any intensity)
# splits in invidiaudla storms to hurricanes and all else. If an individual storm was bot bleow and a husrrcian and a hurricane in teh subste it mark it as a hurricane

remove_200<-unique(t$Key)
 
h<-t%>% group_by(Key) %>% filter(any(Status== "HU"))
t<-t %>% subset(., !(Key %in% unique(h$Key)))%>% group_by(Key)

t<-group_split(t)
t<-lapply(t, as.data.frame)

h<-group_split(h)
h<-lapply(h, as.data.frame)

# need to convert above using to this-> https://stackoverflow.com/questions/29648907/using-geom-rect-for-time-series-shading-in-r

start<-vector(mode="character", length=length(h))
end<-vector(mode="character", length=length(h))
pres<-vector(mode="integer", length=length(h))

for(i in 1:length(h)){
  start[[i]]<-as.character(min(h[[i]]$DateTime))
  end[[i]]<-as.character(max(h[[i]]$DateTime))
  pres[[i]]<-median(h[[i]]$Pressure)
  # pres[[i]]<-min(h[[i]]$Pressure)
}

h_rect<-data.frame(start=date(start), end=date(end), y1=-Inf, y2=pres)

start<-vector(mode="character", length=length(t))
end<-vector(mode="character", length=length(t))
pres<-vector(mode="integer", length=length(t))

for(i in 1:length(t)){
  start[[i]]<-as.character(min(t[[i]]$DateTime))
  end[[i]]<-as.character(max(t[[i]]$DateTime))
  pres[[i]]<-median(t[[i]]$Pressure)
  #   
}

t_rect<-data.frame(start=date(start), end=date(end), y1=-Inf, y2=pres)
rm(t,h)



#standar atmospheirc presures in millibars


```

# 400 km storms only

so 400 with 200 excluded.. prob

```{r}
setwd(wd)
setwd(robj)


h<-readRDS("hurdat.R")
h$DateTime<-with_tz(h$DateTime, tz="UTC")

radii<-100000 ## radius in km for POC select

radii<-2*radii ## for selecting TC that intersect

stations_positions_list<-readRDS("OC1806A_stations_positions_list.R")

st<-stations_positions_list[[3]][4,cbind(2,3)]
st<-sf::st_as_sf(st, coords =c("longitude", "latitude"),  crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
flat<-sf::st_transform(st, "+proj=aeqd +lat_0=18.5005 +lon_0=-108.502" )
circle_3.5_400km<-sf::st_buffer(flat, dist=radii)%>%sf::st_transform(., "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

bbox<-st_bbox(circle_3.5_400km)

# x<-filter(h, Status == "HU") %>% filter(., DateTime >=date(min(poc$date))-60) # save 'h' in order to adjust function variables if needed.
g<-filter(h, DateTime >=date(min(poc$date))-60) # save 'h' in order to adjust function variables if needed.
g<-h

h.pts<- sf::st_as_sf(g, coords = c("Lon","Lat"), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0") %>% 
sf::st_crop(., c(xmin=bbox$xmin[[1]], ymin=bbox$ymin[[1]], xmax=bbox$xmax[[1]], ymax=bbox$ymax[[1]])) #subset by user defined 

# h.pts<-st_difference(h.pts, st_combine(st_geometry(cl))) # remove all points over land
rm(g, poc)

t_4<-h.pts 
st_geometry(t_4)<-NULL
t_4$ymin<--Inf
t_4$ymax<-Inf
# t$DateTime<-as.Date(t$DateTime)
t_4$DateTime<-as_datetime(t_4$DateTime)


#commneted out below. for paper statistics only
h_4<-t_4 %>% subset(., !(Key %in% remove_200))
h_4_all<-t_4

t_4<-t_4 %>% subset(., !(Key %in% remove_200))%>% group_by(Key)




t_4<-group_split(t_4)
t_4<-lapply(t_4, as.data.frame)

start<-vector(mode="character", length=length(t_4))
end<-vector(mode="character", length=length(t_4))
pres<-vector(mode="integer", length=length(t_4))

for(i in 1:length(t_4)){
  start[[i]]<-as.character(min(t_4[[i]]$DateTime))
  end[[i]]<-as.character(max(t_4[[i]]$DateTime))
  pres[[i]]<-median(t_4[[i]]$Pressure)
  #
}

t_4_rect<-data.frame(start=date(start), end=date(end), y1=-Inf, y2=pres)

# uncomment for streamlining
# rm(remove_200)


```

# new plots
* use mee
## definig plot varibales

## option 1

* fig4/online: export and storms (including 400km)

### define plots
```{r}

w<-inner_join(x,y, by='date') %>% inner_join(., z,  by='date' ) %>% select(., - ef)
# rm(poc, chl, sst)

#save original for scale etc
rects<-vector(mode="list")
rects$t<-t_rect
rects$h<-h_rect
rects$t_4<-t_4_rect


 # rectangel parameters:
rect_color<-"white"
sz<-0.25
alph<-.25
# rect_fill<-"cornsilk1" 
rect_fill<-"#fc8d62"
rect_fill_non<-"#8da0cb"
# rect_fill_outside<-"#66c2a5"
 # rect_fill_outside<-"grey48"
rect_fill_outside<-"gray38"


# line colors

line_col<-"#66c2a5"
line_col<-"black"
tcolor<-"red"
chcolor<-"darkgreen"

# title<-paste0("Station ", "3.5", ": ", "Export Flux and storms within 400km^2 box")
# title<-expression(Station~3.5:~Export~Flux~and~storms~within~400*km^2~box)

ylab<-expression(Export~flux~(mgC~m^-2~day^-1))
ylab2<-"Cyclone eye pressure - millibars (mb)"
fig4_txt<-list(ylab, ylab2)
names(fig4_txt)<-c("ylab", "ylab2")



```


## v1
```{r}
txt<-fig4_txt

w<-inner_join(x,y, by='date') %>% inner_join(., z, by='date' ) %>% select(., - ef)
h_rect<-rects$h
t_rect<-rects$t
t_4_rect<-rects$t_4

stdp<-1013.25
ff<-1.745
adj<-stdp+ff*(stdp-min(h_rect$y2))

h_rect$y2<-abs(h_rect$y2-adj)
t_rect$y2<-abs(t_rect$y2-adj)
t_4_rect$y2<-abs(t_4_rect$y2-adj)

g.breaks<-c( 872, 900, 920, plyr::round_any((944+920)/2, 5, f=floor), plyr::round_any((964+945)/2, 5, f=ceiling), plyr::round_any((979+965)/2,5, f=floor), 980, 1000) %>% round(., 0) %>% append(., c(round(stdp,2),  round(adj,2)))

labs<-(g.breaks)
g.breaks<-abs(g.breaks-adj)

t_4_rect<-filter(t_4_rect, start >=date(min(w$date)))
t_rect<-filter(t_rect, start >=date(min(w$date)))
h_rect<-filter(h_rect, start >=date(min(w$date)))

scale.g<-(max(w$avg)/max(c(t_rect$y2, h_rect$y2, t_4_rect$y2)))


plot_v1<-ggplot()+ theme_bw()+
geom_segment(data=t_4_rect, mapping=aes(x=start, xend=end, yend=y2*scale.g, y=-Inf), linetype ="dashed", color=rect_fill_outside, alpha=.5)+  
geom_hline(yintercept=(mean(w$avg)), data=w, linetype="dashed", color ="black")+
geom_rect(data=t_rect, mapping=aes(xmin=start, xmax=end, ymin=-Inf, ymax=y2*scale.g), color=rect_fill_non, fill=rect_fill_non, alpha=.5)+
geom_rect(data=h_rect, mapping=aes(xmin=start, xmax=end, ymin=-Inf, ymax=y2*scale.g), color=rect_fill, fill=rect_fill, alpha=.5)+ 
geom_point(data=w, aes(date, avg), color="black", lwd=.6)+
geom_line(data=w, aes(date, avg), color="black", lwd=0.4)+
scale_y_continuous(name =txt$ylab, sec.axis = sec_axis(~./scale.g, name=txt$ylab2,  breaks = g.breaks , labels= labs))+
# scale_x_date(date_breaks = "1 years", date_labels = "%Y", date_minor_breaks = "6 months", position = "top")+
# scale_x_date(date_breaks = "1 years", date_labels = "%Y", date_minor_breaks = "6 months", position = "top", limits = date(c("2002-01-01","2022-06-01")))+
# scale_x_date(limits = as.Date(c('2002-01-01', '2022-06-01')), date_breaks = "1 years", date_labels = "%Y", date_minor_breaks = "6 months", position = "top")+
# scale_x_date(limits = as.Date(c('2002-01-01', '2022-01-01')), date_breaks = "1 years", date_labels = "%Y", position = "top")+
scale_x_date(limits = as.Date(c('2002-05-01', '2022-02-01')), date_breaks = "1 years", date_labels = "%Y", position = "top", expand = c(0, 0))+
theme(axis.title.x=element_blank(), plot.tag = element_text(face = "bold"))



# expand = c(0, 0))
# 
# limits = as.Date(c('1/1/2002', '6/1/2022'))


```


### saving figure v1

```{r}

number_h_ratio<-33/7


setwd(wd)
setwd(fig)
pdf("figure_four_v1.pdf", height=number_h_ratio , width =14)
plot_v1
dev.off()
```

## v2 

```{r}
txt<-fig4_txt

w<-inner_join(x,y, by='date') %>% inner_join(., z, by='date' ) %>% select(., - ef)
h_rect<-rects$h
t_rect<-rects$t
t_4_rect<-rects$t_4

stdp<-1013.25
ff<-1.745
adj<-stdp+ff*(stdp-min(h_rect$y2))

h_rect$y2<-abs(h_rect$y2-adj)
t_rect$y2<-abs(t_rect$y2-adj)
t_4_rect$y2<-abs(t_4_rect$y2-adj)

g.breaks<-c( 872, 900, 920, plyr::round_any((944+920)/2, 5, f=floor), plyr::round_any((964+945)/2, 5, f=ceiling), plyr::round_any((979+965)/2,5, f=floor), 980, 1000) %>% round(., 0) %>% append(., c(round(stdp,2),  round(adj,2)))

labs<-(g.breaks)
g.breaks<-abs(g.breaks-adj)

t_4_rect<-filter(t_4_rect, start >=date(min(w$date)))
t_rect<-filter(t_rect, start >=date(min(w$date)))
h_rect<-filter(h_rect, start >=date(min(w$date)))

scale.g<-(max(w$avg)/max(c(t_rect$y2, h_rect$y2, t_4_rect$y2)))


plot_v2<-ggplot()+ theme_bw()+
# geom_segment(data=t_4_rect, mapping=aes(x=start, xend=end, yend=y2*scale.g, y=-Inf), linetype ="dashed", color=rect_fill_outside, alpha=.5)+  
geom_hline(yintercept=(mean(w$avg)), data=w, linetype="dashed", color ="black")+
geom_rect(data=t_rect, mapping=aes(xmin=start, xmax=end, ymin=-Inf, ymax=y2*scale.g), color=rect_fill_non, fill=rect_fill_non, alpha=.5)+
geom_rect(data=h_rect, mapping=aes(xmin=start, xmax=end, ymin=-Inf, ymax=y2*scale.g), color=rect_fill, fill=rect_fill, alpha=.5)+ 
geom_point(data=w, aes(date, avg), color="black", lwd=.6)+
geom_line(data=w, aes(date, avg), color="black", lwd=0.4)+
scale_y_continuous(name =txt$ylab, sec.axis = sec_axis(~./scale.g, name=txt$ylab2,  breaks = g.breaks , labels= labs))+
scale_x_date(limits = as.Date(c('2002-05-01', '2022-02-01')), date_breaks = "1 years", date_labels = "%Y", position = "top", expand = c(0, 0))+
theme(axis.title.x=element_blank(), plot.tag = element_text(face = "bold"))



# expand = c(0, 0))
# 
# limits = as.Date(c('1/1/2002', '6/1/2022'))


```


### saving figure v1

```{r}

number_h_ratio<-33/7


setwd(wd)
setwd(fig)
pdf("figure_four_v2.pdf", height=number_h_ratio , width =14)
plot_v2
dev.off()
```

